### 2022-07-05 paper/Manuscript.Rmd
Start Manuscript

---
title: "Frame Competition"
author: "Nicolai Berk"
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    toc: false
    fig_caption: yes
    includes:
      in_header: preamble.tex
subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
fontsize: 12pt
geometry: margin=1.5in
abstract: "Issue ownership theory assumes that the salience of specific issues is always more or less beneficial to a given party. I introduce the concept of 'frame competition' and argue that a given issue can be more or less beneficial for parties dependent on the dominant framing. I test this argument using data from the German 2017 Bundestag campaign, assessing the similarity of media coverage on migration to the parties' migration framing with topic vectors. Using VAR models, I show whether higher frame similarity is associated with better performance in the polls. The findings broaden our understanding party competition and show parties' capability to compete when the issue agenda is given."
bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
---

# Introduction

One of the most prominent explanations for parties' electoral success in scholarly and public debate is the issue agenda at a given election: the more prominent an issue was among political parties, news media, and voters, the more it would influence the latter's electoral decision making. Certain issues are therefor more favorable to given parties and parties will try to focus on 'their' issues in public communication [@Budge1983; @Petrocik1996; @Walgrave2015]. In extension, it is assumed that the main form of electoral competition in contemporary Western European democracies is *issue competition*, in the sense that parties compete to bring 'their' issue on the agenda [@GreenPedersen2019].

The present paper sets out to challenge the truism of 'issue ownership' by looking into the debate *within* issues. Building on a large body of experimental work, I argue that - dependent on the relative emphasis of different considerations in public debate, also known as *emphasis framing* - any issue can be more or less favorable to a given party.  As issues on the media agenda usually emerge externally [@Boydstun2013], issue ownership theory suggests that parties' electoral fate is statically bound to the media agenda of the day. My model of *frame competition* gives parties substantial agency by suggesting that competition takes not only place about *which* issues are talked about, but also *how*.

I test this argument using data from the German 2017 Bundestag campaign, during which the migration issue - which became salient after the 2015 refugee movements - dominated public debate in the media and among parties, as well as voters' perception important problems in national politics. Using topic representations of media content and parties' manifestos as an anchor point, I track the similarity of the migration discourse in national newspapers to parties' communication about migration. Combining these daily similarity estimates with polling data from *Poll of Polls* in a vector auto-regression (VAR) model [@Sims1980], I assess whether parties' electoral prospects increase when the media discourse is more similar to a given party's representation of the migration issue. The findings potentially challenge the current model of party competition, underlining parties' agency even when the agenda is externally determined, and speak to the real-world implications of issue framing.

# Issue Ownership Theory

The classic formulation of issue ownership theory argues that parties 'own' issues when they are peceived as more competent handling the issue [@Budge1983]. If problem pressure on that issue increases and the issue rises to prominence, voters are more likely to base their voting decision on that issue and choose the party that is considered most able to deal with the issue. Over time, scholars have differentiated between this 'competence-based' and an 'associative' form of issue ownership. The latter emphasizes the process of voters' implicit and spontaneous association of an issue with a given party, thereby increasing the likelihood to vote for that party [@Lefevere2015b].

Whichever the mechanism, both conceptualizations imply that parties perform better electorally when 'their' issue is on the top of the agenda, because voters either are more likely to perceive them as the most competent party in the current issue environment or because they are simply more likely to make it to the pool of options in a voters' mind:

*Issue Ownership Hypothesis: The more salient an issue is, the better the electoral prospect of the party owning the issue.*

As mentioned, issue ownership theory assumes that party competition is largely an effort of parties to get 'their' topics on the agenda. As citizens mostly perceive politics in the news media, this means that parties need to bring 'their' issues to the media's attention. However, existing research suggests that the news media rarely follows political actors' attempts to set the agenda, but rather 'leapfrogs' from issue to issue, usually because of external events [@Boydstun2013]. For example, the outbreak of a foreign war, a large movement of refugees, or environmental catastrophes - all events that political parties usually have limited to no control over - might come to dominate the news agenda despite parties' best efforts to talk about redistribution, law and order, or taxation. In this view, parties have ultimately very limited control over their electoral prospects.

# Framing and Party Competition

I suggest that issues can have a differential impact on parties electoral prospects, dependent on *how* they are discussed. Given an issue like migration dominates media coverage, this does not necessarily suggest that the issue owner - typically radical right parties - profits from this electorally. If, for example migration is discussed as a humanitarian issue, e.g. migrants dying at the border, or refugees fleeing war, the issue should favor those parties with more welcoming migration positions more compared to when migration is discussed as a security problem, emphasizing crime and the potential danger of terrorism.

Consider the example in figure \@ref(fig:afdmigration) below. The top panel shows the weekly share of news articles devoted to migration in the major German daily newspapers, from January 2015 to June 2016. As we can see, attention to migration experiences a huge increase in September 2015, when the decision was made to let refugees stranded at Keletti station in Budapest, Hungary, pass to Germany. Issue Ownership theory suggests that this large increase in salience should directly translate into electoral support for the issue owner - in this case, the radical right *AfD*.

```{r afdmigration}
library(tidyverse)
library(here)
library(patchwork)
library(data.table)

# plot afd polling
de_polls <- 
  rjson::fromJSON(file = "https://www.politico.eu/wp-json/politico/v1/poll-of-polls/DE-parliament")$polls

de_polls_df <- data.frame()

for (row in de_polls){

  row <- as.data.frame(row)

  row$sample_size <- as.numeric(row$sample_size)

  de_polls_df <- 
    bind_rows(
      de_polls_df,
      row)

}

afd_poll_plot <- 
  de_polls_df %>% 
  mutate(date = as.Date(date)) %>% 
  filter(date < as.Date("2016-07-01"),
         date >= as.Date("2015-01-01")) %>% 
  mutate(week = lubridate::floor_date(date, "week")
         # , post = date >= as.Date("2016-01-01")
         ) %>% 
  group_by(week
           # , post
           ) %>% 
  summarise(parties.AfD = mean(parties.AfD)) %>% 
  ggplot(aes(week, parties.AfD
             # , group = post
             )) +
  geom_point() +
  geom_smooth(method = "gam") +
  # geom_vline(xintercept = as.Date("2015-09-01"), col = "red", lty = 2) +
  theme_minimal() +
  ylab("AfD vote share") +
  xlab("Date")

# plot media attention to migration - add spon if possible
mig_salience_plot <- 
  fread(here("data/media/bert_crime_daily.csv")) %>% 
  select(date_clean, paper, mig_share) %>% 
  mutate(date_new = lubridate::floor_date(date_clean, "week")) %>% 
  group_by(date_new, paper) %>% 
  summarise_all(mean) %>% 
  filter(date_new < as.Date('2016-07-01'),
         date_new >= as.Date("2015-01-01")) %>%
  ggplot(aes(x = date_new, y = mig_share, col = paper, lty = paper, shape = paper)) +
  geom_line() + geom_point() +
  # geom_vline(xintercept = as.Date("2015-09-01"), col = "red", lty = 2) +
  ggtitle('Migration salience in different newspapers') +
  xlab('') + ylab('Share of migration articles') +
  theme_minimal() +
  labs(color = "Outlet", lty = "Outlet", shape = "Outlet")

mig_salience_plot / afd_poll_plot

```

The AfD's electoral prospect as reported in opinion polls is plotted in the panel below, for the same time frame. As we can see, the increase in voting intention for the radical right party trails the increase in salience by several months. Why might that be? Is it really the case that it took voters three to six months to understand that migration was a pressing issue on the political agenda, despite the omnipresence of the issue in the news media? I suggest another explanation, which points to the changing *content* of the migration discourse. While the media coverage in the early stages of the refugee movements in 2015 focused on the tragic drownings in the Mediterranean sea, reasons for refugees' escape from their home countries, and humanitarian issues, the discourse slowly shifted to focus on perceived problems with the newly arrived. Especially new years eve 2015/16 marked a turning point, when hundreds of sexual abuses by men whom the victims perceived to be of arabic descent in Cologne were reported (if you look closely, you can see a slight discontinuity surrounding that date in the AfD-share, which increases around one and a half percentage points at that very date).

To be clear, I do not suggest that the salience of issues does not matter. Existing preferences in the electorate surely make certain issues more or less favourable for given parties at a specific moment in time. However, I suggest that the *content* of the public debate surrounding an issue shapes the mental representations of this issue in the electorate, and subsequently affects both their issue preferences and their voting behaviour. This would have profound implications for our understanding of party competition. For example, parties' strategic options look very different through this theoretical lens. Rather than remaining mute on unfortunate issues and accepting a fate determined by an uncontrollable media agenda, parties should communicate on any issue and promote arguments that bolster their position on this issue. Similarly, public preferences on an issue are not simply given *a priori*, but rather shaped by the considerations brought up in a changing public discourse.

How could changing issue content be described in a theoretical model? The next section introduces the concept of emphasis framing and the value-expectancy model of preference formation. This theoretical framework allows me to formulate clear expectations about the impact of changing issue content on voting behaviour, as well as clarify the concepts to be operationalised.

## The Value-Expenctancy Framework and Emphasis Framing

<!-- <explain Ajzen-Fishbein model> -->

*Frame Competition Hypothesis: The more similar an issue's framing to a given parties' issue framing, the better that parties' electoral prospect.*

Different from Meguid salience X position model: it is the media, not the party that moves!!

# Research Design

## The Migration Issue in the German Bundestagswahl 2017

## Measuring Parties' Preferred Issue Framing

## Measuring Frame Similarity

## Estimating the Effect of Frame Similarity on Electoral Prospects

### 2022-07-05 paper/Manuscript.Rmd
Add explanation of expectancy-value model

@@
 
-<!-- <explain Ajzen-Fishbein model> -->
+What aspect of news content affect political preferences?
+Specifically, how can different considerations about the same issue affect one's reasoning and preferences regarding that issue?
+The large and established literature on framing has tackled precisely this question.
+To be clear, when I speak of "framing" in this manuscript, I refer to *emphasis framing*.
+Compared to concepts like equivalence frames (outlining different formulations of mathematically identical options; @Kahnemann1970), generic frames (portraying complex issues, e.g.
+elections within common and simplified metaphors, e.g.
+as a horse race; @DeVreese2005), or episodic frames (portraying issues through individual, personal stories; @Iyengar2005), emphasis framing focuses on the *emphasis* of different *considerations* surrounding an issue.
+For example, discussing the issue of migration, the debate can focus on the brutal reality of refugees' lifes and the hardships they face on their escape; or the discourse might focus on fears of the population in host countries and potential problems in the accommodation of refugees.
+The emphasis of different considerations will create different mental images which lead to differing assessments of the problem at hand, different preferences about the issue, and a different set of potential policy solutions.
+
+More formally, this logic is expressed in the *value-expectancy framework* of attitude formation [@Ajzen2000; @Nelson1997].
+An attitude towards a political issue is a function of two things in this model: first, different considerations contain a certain positive or negative evaluation of the issue (let's call this $e_i$).
+For example, thinking of how to deal with criminal refugees will entail a more restrictive assessment towards immigration policy (simplistically $e_1 = -1$), whereas reasoning about how to prevent the humanitarian tragedies in the Mediterranean sea should be associated with a more welcoming position ($e_2 = 1$).
+All available considerations are then weighted by the *strength of the association* with the issue.
+That is, if an individual associates the issue of migration more strongly with criminal migrants rather than drownings in the Mediterranean sea, they weigh the former consideration more strongly ($w_1 = 0.9$) than the second ($w_2 = 0.1$) to form their overall opinion on the issue.
+The overall attitude $y$ is then a weighted sum of each consideration ($\sum_{i = 1}{e_i*w_i}$), or in this case $-1*0.9 + 1*0.1 = -0.8$.
+Given the stronger weighting of the consideration of criminal migrants by the respondent, the overall formed attitude is a negative/restrictive one.
+
+## Emphasis Framing, the Media, and Party Competition
+
+How does the media play into this? And how does this translate in to voting behaviour?
 

### 2022-07-05 paper/Manuscript.Rmd
Add section on framing, media and party competition

@@
 The classic formulation of issue ownership theory argues that parties 'own' issues when they are peceived as more competent handling the issue [@Budge1983].
-If problem pressure on that issue increases and the issue rises to prominence, voters are more likely to base their voting decision on that issue and choose the party that is considered most able to deal with the issue.
+If the problem pressure regarding that issue increases and the issue rises to prominence, voters are more likely to base their voting decision on that issue and choose the party that is considered most able to deal with the issue.
 Over time, scholars have differentiated between this 'competence-based' and an 'associative' form of issue ownership.
@@
 
-How does the media play into this? And how does this translate in to voting behaviour?
+How does the media play into this?
+And how does this translate in to voting behaviour?
+The distinction of *frames in mind* and *frames in communication* is helpful [@Druckman2001].
+*Frames in mind* describe the association mentioned above - a cognitive process where a given issue is associated with a specific consideration.
+*Frames in communication*, on the other hand, are located in political communication and are defined by the emphasis of one or several considerations in relation to an issue.
+Frames in communication change frames in mind by strengthening the association between an issue and a consideration, thereby affecting the cognitive definition of the issue and the resulting attitude towards this political issue.
+Hence, at least in theory, the media is able to change public opinion by emphasising different considerations about an issue.
 
-*Frame Competition Hypothesis: The more similar an issue's framing to a given parties' issue framing, the better that parties' electoral prospect.*
+How do changing issue attitudes translate into support for political parties?
+Similar to issue ownership theory, the theory here assumes that voters are more likely to incorporate a given issue in their voting decision if that issue is currently in public debate.
+However, dependent on the considerations that dominate public debate about this issue, parties' positions will be more or less favored.
+To stick with the migration example: while issue ownership theory assumes that the salience of migration will *always* favor radical right parties as the owner of that issue, the proposed theory suggests that which party profits from the increased salience of migration is also dependent on the considerations salient in the debate.
+If migrant crime is the dominating consideration, surely a radical right parties' restrictive positions will be supported and voters will be inclined to vote for this party.
+If however humanitarian issues dominate the debate, voters' cognitive representation of the issue should lead them to welcome more liberal positions on immigration policy, which should favor the radical right less and parties with more left-leaning positions more.
 
-Different from Meguid salience X position model: it is the media, not the party that moves!!
+Lastly, I should mention that I assume that parties emphasise issue considerations in line with their political positions.
+That does not necessarily entail rationality (instead of a strategic effort to substantiate their positions, parties might also hold certain policy positions because they emphasize certain considerations), but is a (weak) assumption that should be mentioned here.
+Given that parties promote issue considerations supporting their positions, I can assume that when the news media emphasises considerations about a salient issue similar to that of the party, this party should experience increasing electoral support:
+
+*Frame Competition Hypothesis: The more similar an medis's framing of an issue to a given parties' issue framing, the better that parties' electoral prospect.*
+
+One key difference compared to other models of party competition, especially the one described in @Meguid2009 is that in the present model, party positions are considered fixed, while it is the media debate that moves.
+Large shifts in parties' issue positions are generally rare [@SOURCE], but the media debate is in permanent flux, promoting a constantly changing set of issues and related considerations to voters.
+While the classic model described in @Meguid2009 views parties' electoral performance as a function of parties position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasised by the party to substantiate its position:
+
+[insert formula]
 

### 2022-07-06 paper/Manuscript.Rmd
Fix plot display

@@
 ---
+
+```{r setup, include = F}
+
+knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.height=6, fig.width=10, fig.align='center', eval = T)
+
+library(tidyverse)
+library(dplyr)
+library(data.table)
+library(patchwork)
+library(here)
+
+# load self-made functions
+for (filename in list.files(here("code/functions"))){
+  source(here(paste0('code/functions/', filename)))
+}
+
+```
 
@@
 
-```{r afdmigration}
-library(tidyverse)
-library(here)
-library(patchwork)
-library(data.table)
+```{r afdmigration, fig.height = 10}
 
@@
 
-*Frame Competition Hypothesis: The more similar an medis's framing of an issue to a given parties' issue framing, the better that parties' electoral prospect.*
+*Frame Competition Hypothesis: The more similar the media's framing of an issue to a given parties' issue framing, the better that parties' electoral prospect.*
 
-One key difference compared to other models of party competition, especially the one described in @Meguid2009 is that in the present model, party positions are considered fixed, while it is the media debate that moves.
+One key difference compared to other models of party competition, especially the one described in @Meguid2005 is that in the present model, party positions are considered fixed, while it is the media debate that moves.
 Large shifts in parties' issue positions are generally rare [@SOURCE], but the media debate is in permanent flux, promoting a constantly changing set of issues and related considerations to voters.
-While the classic model described in @Meguid2009 views parties' electoral performance as a function of parties position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasised by the party to substantiate its position:
-
-[insert formula]
+Political actors sponsor frames and arguments, only some of which get to influence the debate.
+While the classic model described in @Meguid2005 views parties' electoral performance as a function of parties position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasised by the party to substantiate its position.
 
@@
 ## Estimating the Effect of Frame Similarity on Electoral Prospects
+
+## Instrumenting Frame Attention

### 2022-07-06 paper/Manuscript.Rmd
Add empirical strategy

@@
 One of the most prominent explanations for parties' electoral success in scholarly and public debate is the issue agenda at a given election: the more prominent an issue was among political parties, news media, and voters, the more it would influence the latter's electoral decision making.
-Certain issues are therefor more favorable to given parties and parties will try to focus on 'their' issues in public communication [@Budge1983; @Petrocik1996; @Walgrave2015].
+Certain issues are therefor more favorable to given parties and parties will try to focus on 'their' issues in public communication [@Budge1983; @Petrocik1996; @Walgrave2012].
 In extension, it is assumed that the main form of electoral competition in contemporary Western European democracies is *issue competition*, in the sense that parties compete to bring 'their' issue on the agenda [@GreenPedersen2019].
@@
 
-## The Value-Expenctancy Framework and Emphasis Framing
+## The Value-Expectancy Framework and Emphasis Framing
 
@@
 To be clear, when I speak of "framing" in this manuscript, I refer to *emphasis framing*.
-Compared to concepts like equivalence frames (outlining different formulations of mathematically identical options; @Kahnemann1970), generic frames (portraying complex issues, e.g.
+Compared to concepts like equivalence frames (outlining different formulations of mathematically identical options; @Kahneman1979prospect, generic frames (portraying complex issues, e.g.
 elections within common and simplified metaphors, e.g.
@@
 
-More formally, this logic is expressed in the *value-expectancy framework* of attitude formation [@Ajzen2000; @Nelson1997].
+More formally, this logic is expressed in the *value-expectancy framework* of attitude formation [@Ajzen2000; @Nelson1997Rally].
 An attitude towards a political issue is a function of two things in this model: first, different considerations contain a certain positive or negative evaluation of the issue (let's call this $e_i$).
@@
 Political actors sponsor frames and arguments, only some of which get to influence the debate.
-While the classic model described in @Meguid2005 views parties' electoral performance as a function of parties position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasised by the party to substantiate its position.
+While the classic model described in @Meguid2005 views parties' electoral performance as a function of parties position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasized by the party to substantiate its position.
 
@@
 
-## The Migration Issue in the German Bundestagswahl 2017
+## The German *Bundestagswahl* 2017[^1]
 
-## Measuring Parties' Preferred Issue Framing
+[^1]: I am not entirely sure if it is smart to restrict myself to the 2017 campaign, as there should be more variation over time, especially moving from late 2015 to 2016, as described above.
+So far, this was a choice entirely made based on the use of the 2017 manifestos, but I might also combine the 2013 and 2017 manifestos and track the issue across time.
+
+In order to study whether framing can change parties' electoral prospects, an ideal case would show substantial variation surrounding the framing of an issue but little variation in parties' positions.
+Ideally, the variation in salience would be limited and uncorrelated to the variation of the framing.
+I choose the case of the election campaign for the German Bundestagswahl 2017 as I consider most of these criteria are met.
+After the refugee movements throughout Europe in 2015, voters considered migration the most important issue [@Wessels2021, p.
+12], and the media still discussed the issue, but at lower levels compared to 2017 (see figure \@ref(fig:salplot)).
+I expect that events during the election campaign, such as migrant crimes, conflicts regarding the intra-EU distribution of refugees, international terrorism, humanitarian crises as those among the Rohingya in Myanmar, as well as drownings in the Mediterranean sea lead to substantial variation in the considerations regarding migration being discussed - the key independent variable.
+
+```{r salplot}
+
+fread(here("data/media/bert_crime_daily.csv")) %>% 
+  select(date_clean, mig_share) %>% 
+  mutate(date_new = lubridate::floor_date(date_clean, "month")) %>% 
+  group_by(date_new) %>% 
+  summarise_all(mean) %>% 
+  filter(date_new < as.Date('2018-01-01'),
+         date_new >= as.Date("2014-01-01")) %>%
+  ggplot(aes(x = date_new, y = mig_share)) +
+  geom_line() + geom_point() +
+  geom_vline(xintercept = as.Date("2017-09-24"), col = "red", lty = 2) +
+  ggtitle('Migration salience in print media', '2014-2017, red line indicates 2017 election') +
+  xlab('') + ylab('Share of migration articles') +
+  theme_minimal()
+
+```
+
+## Measuring Migration Framing in the Media
+
+How can such a diffuse concept as issue framing be measured?
+In order to identify different considerations in media coverage, I will use a two-step approach.
+After training a neural network (BERT) to classify migration content in news coverage (providing a measure of salience), I employ the structural topic model[^2] [@Roberts2019], to identify different topics being raised *within* migration coverage.
+This model allows to specify covariates, such as different prevalence of frames across newspapers.
+The topic model might for example identify topics like crime, terrorism, refugee deaths, and the distribution of refugees.
+Each of these topics represents a consideration about migration, which will have implications for the evaluation of the issue.
+
+[^2]: At this point, I am not sure if I might not instead use a simple LDA.
+
+The topic model then returns a topic vector for each news article, representing the distribution of topics in each article.
+For example, an article might talk to 90% about crime and 10% about the distribution of refugees, whereas it does not mention refugee deaths or terrorism.
+In this hypothetical four-topic space, the article would then be represented by a $[0.9, 0.1, 0, 0]$ vector, much like an embedding.
 
@@
 
+In order to avoid making assumptions about the favorability of different considerations for different parties, I exploit this embedding-like structure of topic vectors to assess their similarity to party communication.
+The assumption I make instead is that party positions on migration are stable across the campaign, and that parties emphasize considerations supporting their position on the issue of migration.
+To measure the emphasis of different considerations in party communication, I select all paragraphs from parties' election manifestos in the 2017 election that are concerned with migration.
+For each party, I generate a topic vector using the model described in section, based on the collection of all relevant paragraphs \@ref(measuring-migration-framing-in-the-media).
+
+Now, using these party-framing vectors, *I can assess the similarity of each news article towards each party's migration framing, simply by taking the cosine distance to the party's vector*.
+This way, it is possible to track the similarity of the media framing of migration to each party, in order to test the frame competition hypothesis: whether parties perform better when the media framing of migration is more similar to their own framing.
+This could well be done with document embeddings as well, however topic vectors offer a key advantage here: other than the dimensions of a, say, 300-dimensional embedding model, the dimensions of topic-vectors are interpretable.
+This can serve as a sanity check (e.g.
+if increased attention to crime results in higher similarity to a left-wing party that supports extended immigration, this would suggest that the model is not great), as well as enrich the data analysis: if frame similarity has an effect on parties' electoral prospects, it is easy to see which topics drive this effect and how the media debate affected opinion polls.
+
 ## Estimating the Effect of Frame Similarity on Electoral Prospects
 
+As the above approach will provide me with time-series data on the similarity of the public debate surrounding migration to each parties' definition of migration, and given the time-series structure of the polling data (the dependent variable), it seems straightforward to use time-series modeling, and specifically vector-auto-regression (VAR) models[^3] [@Sims1980] to account for possible effects of the polls on media reporting about migration.
+
+[^3]: As I never used VAR models to model interaction effects, I am not entirely sure how to account for variation in salience here.
+It might still be possible to use split samples of periods with higher and lower salience, or restrict the analysis to a period with relatively stable attention to migration (e.g.
+just the election campaign).
+
 ## Instrumenting Frame Attention
+
+An additional possibility in order to improve causal identification was to use exogenous events like the new years eve in cologne, terrorist attacks abroad or drownings in the Mediterranean sea to instrument attention to specific topics.
+This idea has not far progressed, so I am curious about your thoughts on this.

### 2022-07-06 paper/Manuscript.Rmd
Add 3d plot

@@
 Now, using these party-framing vectors, *I can assess the similarity of each news article towards each party's migration framing, simply by taking the cosine distance to the party's vector*.
-This way, it is possible to track the similarity of the media framing of migration to each party, in order to test the frame competition hypothesis: whether parties perform better when the media framing of migration is more similar to their own framing.
+Figure \@ref(fig:vectors) gives an example: the article vector (representing the distribution of different topics within the article) is clearly closer to the vector of party a (representing the distribution of topics in party a's communication), compared to party b.
+
+With this approach, it is possible to track the similarity of the media framing of migration to each party, in order to test the frame competition hypothesis: whether parties perform better when the media framing of migration is more similar to their own framing.
 This could well be done with document embeddings as well, however topic vectors offer a key advantage here: other than the dimensions of a, say, 300-dimensional embedding model, the dimensions of topic-vectors are interpretable.
@@
 if increased attention to crime results in higher similarity to a left-wing party that supports extended immigration, this would suggest that the model is not great), as well as enrich the data analysis: if frame similarity has an effect on parties' electoral prospects, it is easy to see which topics drive this effect and how the media debate affected opinion polls.
+
+```{r vectors}
+
+library(plotly)
+
+item <- c("article", "Party A", "Party B",
+          "article", "Party A", "Party B")
+dim1 <- c(0,  0.2, 0.8,
+          0,0,0)
+dim2 <- c(.8, 0.8, 0.2,
+          0,0,0)
+dim3 <- c(.5, 0.8, 0.8,
+          0,0,0)
+
+plot_ly(x = dim1, y = dim2, z = dim3, 
+        color = item, linetype = item,
+        type = "scatter3d", mode = "lines")
+
+```
 
@@
 This idea has not far progressed, so I am curious about your thoughts on this.
+
+# Resources

### 2022-07-06 paper/Manuscript.Rmd
Update vector plot and descriptions

--- 2022-07-06 paper/Manuscript.Rmd
@@
 Now, using these party-framing vectors, *I can assess the similarity of each news article towards each party's migration framing, simply by taking the cosine distance to the party's vector*.
-This way, it is possible to track the similarity of the media framing of migration to each party, in order to test the frame competition hypothesis: whether parties perform better when the media framing of migration is more similar to their own framing.
+Figure \@ref(fig:vectors) gives a two-dimensional example: the article vector (representing the distribution of different considerations within the article) is clearly closer to the vector of party a (representing the distribution of considerations in party a's communication), compared to party b.
+
+With this approach, it is possible to track the similarity of the media framing of migration to each party, in order to test the frame competition hypothesis: whether parties perform better when the media framing of migration is more similar to their own framing.
 This could well be done with document embeddings as well, however topic vectors offer a key advantage here: other than the dimensions of a, say, 300-dimensional embedding model, the dimensions of topic-vectors are interpretable.
@@
 if increased attention to crime results in higher similarity to a left-wing party that supports extended immigration, this would suggest that the model is not great), as well as enrich the data analysis: if frame similarity has an effect on parties' electoral prospects, it is easy to see which topics drive this effect and how the media debate affected opinion polls.
+
+```{r vectors}
+
+data.frame(
+  item = c("article", "Party A", "Party B",
+            "article", "Party A", "Party B"),
+  dim1 = c(0,  0.2, 0.8,
+            0,0,0),
+  dim2 = c(1, 0.8, 0.2,
+            0,0,0)
+) %>% 
+ggplot(aes(x = dim1, y = dim2, 
+        color = item, linetype = item)) +
+  geom_line() +
+  geom_point(alpha = 0.3) + 
+  theme_minimal() +
+  xlab("Attention to Consideration 1") +
+  ylab("Attention to Consideration 2") +
+  theme(legend.title = element_blank())
+
+```
 

### 2022-07-07 paper/Manuscript.Rmd
Clarify instrument idea
Proofread, add figure captions, specify instrument

@@
       in_header: preamble.tex
-subtitle: Manuscript prepared for the 12th Annual Conference of the European Political Science Association in Prague, Czech Republic
+subtitle: Manuscript prepared for the OX|BER workshop, Berlin, July 14th-15th.
 fontsize: 12pt
@@
 I introduce the concept of 'frame competition' and argue that a given issue can be more or less beneficial for parties dependent on the dominant framing.
-I test this argument using data from the German 2017 Bundestag campaign, assessing the similarity of media coverage on migration to the parties' migration framing with topic vectors.
-Using VAR models, I show whether higher frame similarity is associated with better performance in the polls.
-The findings broaden our understanding party competition and show parties' capability to compete when the issue agenda is given."
+I test this argument using data from the German 2017 Bundestag campaign, assessing the similarity of media coverage on migration to parties' migration framing with topic vectors.
+Using VAR models and an instrumental variable approach, I show whether higher frame similarity is associated with better performance in the polls.
+The findings broaden our understanding party competition and underline possibilities for political change, as well as parties' capability to compete, even when the issue agenda is given."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 
-The present paper sets out to challenge the truism of 'issue ownership' by looking into the debate *within* issues.
+The present paper sets out to challenge this simple model of issue ownership by looking into party competition *within* issues.
 Building on a large body of experimental work, I argue that - dependent on the relative emphasis of different considerations in public debate, also known as *emphasis framing* - any issue can be more or less favorable to a given party.
 As issues on the media agenda usually emerge externally [@Boydstun2013], issue ownership theory suggests that parties' electoral fate is statically bound to the media agenda of the day.
-My model of *frame competition* gives parties substantial agency by suggesting that competition takes not only place about *which* issues are talked about, but also *how*.
+My model of *frame competition* gives parties substantial agency by suggesting that political actors not only compete over *which* issues are talked about, but also *how*.
 
-I test this argument using data from the German 2017 Bundestag campaign, during which the migration issue - which became salient after the 2015 refugee movements - dominated public debate in the media and among parties, as well as voters' perception important problems in national politics.
+I test this argument using data from the German 2017 Bundestag campaign, during which the immigration issue - which became salient after the 2015 refugee movements - dominated public debate in the media and among parties, as well as voters' perception of the most important problems in national politics.
 Using topic representations of media content and parties' manifestos as an anchor point, I track the similarity of the migration discourse in national newspapers to parties' communication about migration.
-Combining these daily similarity estimates with polling data from *Poll of Polls* in a vector auto-regression (VAR) model [@Sims1980], I assess whether parties' electoral prospects increase when the media discourse is more similar to a given party's representation of the migration issue.
+Combining these daily similarity estimates with polling data from *Poll of Polls*[^1] using vector auto-regression (VAR) models [@Sims1980] and an instrumental variable approach, I assess whether parties' electoral prospects increase when the media discourse is more similar to a given party's representation of the migration issue.
 The findings potentially challenge the current model of party competition, underlining parties' agency even when the agenda is externally determined, and speak to the real-world implications of issue framing.
+More generally, this research locates political opportunity spaces within debates, rather than viewing political competition solely as a game of changing issue attention.
+
+[^1]: \url{https://www.politico.eu/europe-poll-of-polls/}
 
@@
 
-Whichever the mechanism, both conceptualizations imply that parties perform better electorally when 'their' issue is on the top of the agenda, because voters either are more likely to perceive them as the most competent party in the current issue environment or because they are simply more likely to make it to the pool of options in a voters' mind:
+Whichever the mechanism, both conceptualizations imply that parties perform better electorally when 'their' issue is on the top of the agenda, because voters either are more likely to perceive them as the most competent party in the current issue environment or because they are simply more likely to make it to the pool of viable options in a voters' mind:
 
@@
 Given an issue like migration dominates media coverage, this does not necessarily suggest that the issue owner - typically radical right parties - profits from this electorally.
-If, for example migration is discussed as a humanitarian issue, e.g.
+If, for example, migration is discussed as a humanitarian issue, e.g.
 migrants dying at the border, or refugees fleeing war, the issue should favor those parties with more welcoming migration positions more compared to when migration is discussed as a security problem, emphasizing crime and the potential danger of terrorism.
@@
 
-```{r afdmigration, fig.height = 10}
+```{r afdmigration, fig.height = 10, fig.cap="Salience of immigration issue in major German newspapers (top panel) and support for radical-right AfD in 2015/16."}
 
@@
   ylab("AfD vote share") +
-  xlab("Date")
+  xlab("Date") + xlim(as.Date("2015-01-01"), as.Date("2016-07-01")) +
+  ggtitle("Share of respondents indicating support for AfD", "Source: Poll of Polls")
 
@@
   select(date_clean, paper, mig_share) %>% 
-  mutate(date_new = lubridate::floor_date(date_clean, "week")) %>% 
+  mutate(date_new = lubridate::floor_date(date_clean, "month")) %>% 
   group_by(date_new, paper) %>% 
@@
   ggtitle('Migration salience in different newspapers') +
-  xlab('') + ylab('Share of migration articles') +
+  xlab('') + xlim(as.Date("2015-01-01"), as.Date("2016-07-01")) +
+  ylab('Share of migration articles') +
   theme_minimal() +
@@
 As we can see, the increase in voting intention for the radical right party trails the increase in salience by several months.
+In fact, the party experiences a \*low\* right around the peak in immigration coverage.
 Why might that be?
@@
 While the media coverage in the early stages of the refugee movements in 2015 focused on the tragic drownings in the Mediterranean sea, reasons for refugees' escape from their home countries, and humanitarian issues, the discourse slowly shifted to focus on perceived problems with the newly arrived.
-Especially new years eve 2015/16 marked a turning point, when hundreds of sexual abuses by men whom the victims perceived to be of arabic descent in Cologne were reported (if you look closely, you can see a slight discontinuity surrounding that date in the AfD-share, which increases around one and a half percentage points at that very date).
+Especially new years eve 2015/16 marked a turning point, when hundreds of sexual abuses by men whom the victims perceived to be of arabic descent in Cologne were reported (if you look closely, you can see a discontinuity surrounding that date in the AfD-share, which increases around one and a half percentage points at that very date).
 
@@
 For example, parties' strategic options look very different through this theoretical lens.
-Rather than remaining mute on unfortunate issues and accepting a fate determined by an uncontrollable media agenda, parties should communicate on any issue and promote arguments that bolster their position on this issue.
+Rather than remaining mute on unfortunate issues and desperately trying to change an uncontrollable media agenda, parties should communicate on any issue and promote arguments that bolster their position on this issue.
+Existing research suggests that this is a successful strategy [@Jerit2008].
 Similarly, public preferences on an issue are not simply given *a priori*, but rather shaped by the considerations brought up in a changing public discourse.
@@
 What aspect of news content affect political preferences?
-Specifically, how can different considerations about the same issue affect one's reasoning and preferences regarding that issue?
+Specifically, how can different considerations about the same issue affect voters' reasoning and preferences regarding that issue?
 The large and established literature on framing has tackled precisely this question.
 To be clear, when I speak of "framing" in this manuscript, I refer to *emphasis framing*.
-Compared to concepts like equivalence frames (outlining different formulations of mathematically identical options; @Kahneman1979prospect, generic frames (portraying complex issues, e.g.
-elections within common and simplified metaphors, e.g.
-as a horse race; @DeVreese2005), or episodic frames (portraying issues through individual, personal stories; @Iyengar2005), emphasis framing focuses on the *emphasis* of different *considerations* surrounding an issue.
+Compared to concepts like equivalence frames (outlining different formulations of mathematically identical options; @Kahneman1979prospect ), generic frames (portraying complex issues within common and simplified themes, e.g.
+elections as a horse race; @DeVreese2005), or episodic frames (portraying issues through individual, personal stories; @Iyengar2005), emphasis framing focuses on the *emphasis* of different *considerations* surrounding an issue.
 For example, discussing the issue of migration, the debate can focus on the brutal reality of refugees' lifes and the hardships they face on their escape; or the discourse might focus on fears of the population in host countries and potential problems in the accommodation of refugees.
@@
 An attitude towards a political issue is a function of two things in this model: first, different considerations contain a certain positive or negative evaluation of the issue (let's call this $e_i$).
-For example, thinking of how to deal with criminal refugees will entail a more restrictive assessment towards immigration policy (simplistically $e_1 = -1$), whereas reasoning about how to prevent the humanitarian tragedies in the Mediterranean sea should be associated with a more welcoming position ($e_2 = 1$).
+For example, thinking of how to deal with criminal refugees will entail a more restrictive assessment towards immigration policy (simplistically $e_{Crime} = -1$), whereas reasoning about how to prevent the humanitarian tragedies in the Mediterranean sea should be associated with a more welcoming position ($e_{Tragedy} = 1$).
 All available considerations are then weighted by the *strength of the association* with the issue.
-That is, if an individual associates the issue of migration more strongly with criminal migrants rather than drownings in the Mediterranean sea, they weigh the former consideration more strongly ($w_1 = 0.9$) than the second ($w_2 = 0.1$) to form their overall opinion on the issue.
-The overall attitude $y$ is then a weighted sum of each consideration ($\sum_{i = 1}{e_i*w_i}$), or in this case $-1*0.9 + 1*0.1 = -0.8$.
+That is, if an individual associates the issue of migration more strongly with criminal migrants rather than drownings in the Mediterranean sea, they weigh the former consideration more strongly ($w_{Crime} = 0.9$) than the second ($w_{Tragedy} = 0.1$) to form their overall opinion on the issue.
+The overall attitude $y$ is then a weighted sum of each consideration's evaluation ($\sum_{i = 1}{e_i*w_i}$), or in this case $-1*0.9 + 1*0.1 = -0.8$.
 Given the stronger weighting of the consideration of criminal migrants by the respondent, the overall formed attitude is a negative/restrictive one.
@@
 And how does this translate in to voting behaviour?
-The distinction of *frames in mind* and *frames in communication* is helpful [@Druckman2001].
+The distinction of *frames in mind* and *frames in communication* is helpful here [@Druckman2001].
 *Frames in mind* describe the association mentioned above - a cognitive process where a given issue is associated with a specific consideration.
 *Frames in communication*, on the other hand, are located in political communication and are defined by the emphasis of one or several considerations in relation to an issue.
-Frames in communication change frames in mind by strengthening the association between an issue and a consideration, thereby affecting the cognitive definition of the issue and the resulting attitude towards this political issue.
+Frames in communication change frames in mind by strengthening the association between an issue and a consideration, thereby affecting the cognitive definition of the issue and (according to the formula above) the resulting attitude towards this political issue.
 Hence, at least in theory, the media is able to change public opinion by emphasising different considerations about an issue.
@@
 However, dependent on the considerations that dominate public debate about this issue, parties' positions will be more or less favored.
-To stick with the migration example: while issue ownership theory assumes that the salience of migration will *always* favor radical right parties as the owner of that issue, the proposed theory suggests that which party profits from the increased salience of migration is also dependent on the considerations salient in the debate.
+To stick with the migration example: while issue ownership theory assumes that the salience of migration will *always* favor radical right parties as the owner of that issue, the proposed theory suggests that *which party profits from the increased salience of migration is dependent on the considerations salient in the debate*.
 If migrant crime is the dominating consideration, surely a radical right parties' restrictive positions will be supported and voters will be inclined to vote for this party.
@@
 Lastly, I should mention that I assume that parties emphasise issue considerations in line with their political positions.
-That does not necessarily entail rationality (instead of a strategic effort to substantiate their positions, parties might also hold certain policy positions because they emphasize certain considerations), but is a (weak) assumption that should be mentioned here.
-Given that parties promote issue considerations supporting their positions, I can assume that when the news media emphasises considerations about a salient issue similar to that of the party, this party should experience increasing electoral support:
+That does not necessarily entail rationality: instead of a strategic effort to substantiate their positions, parties might also hold certain policy positions *because* they pay more attention to certain considerations.
+Given that parties promote issue considerations supporting their positions, I expect that when the news media emphasizes the same considerations emphasized by a certain the party, the debate should favor that party's position on the issue more and hence this party should experience increasing electoral support:
 
@@
 Political actors sponsor frames and arguments, only some of which get to influence the debate.
-While the classic model described in @Meguid2005 views parties' electoral performance as a function of parties position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasized by the party to substantiate its position.
+While the classic model described in @Meguid2005 views parties' electoral performance as a function of party position and issue salience, the present model views their electoral performance as a function of issue salience and the similarity of the dominant set of issue considerations to the set of considerations emphasized by the party.
 
@@
 
-## The German *Bundestagswahl* 2017[^1]
+## The German *Bundestagswahl* 2017[^2]
 
-[^1]: I am not entirely sure if it is smart to restrict myself to the 2017 campaign, as there should be more variation over time, especially moving from late 2015 to 2016, as described above.
+[^2]: I am not entirely sure if it is smart to restrict myself to the 2017 campaign, as there should be more variation over time, especially moving from late 2015 to 2016, as described in section \@ref(framing-and-party-competition).
 So far, this was a choice entirely made based on the use of the 2017 manifestos, but I might also combine the 2013 and 2017 manifestos and track the issue across time.
@@
 12], and the media still discussed the issue, but at lower levels compared to 2017 (see figure \@ref(fig:salplot)).
-I expect that events during the election campaign, such as migrant crimes, conflicts regarding the intra-EU distribution of refugees, international terrorism, humanitarian crises as those among the Rohingya in Myanmar, as well as drownings in the Mediterranean sea lead to substantial variation in the considerations regarding migration being discussed - the key independent variable.
+I expect that events during the election campaign, such as migrant crimes, conflicts regarding the intra-EU distribution of refugees, international terrorism, humanitarian crises as those among the Rohingya in Myanmar, as well as drownings in the Mediterranean sea lead to substantial variation in the set of considerations regarding migration being discussed - the key independent variable.
 
-```{r salplot}
+```{r salplot, fig.cap="Salience of the immigration issue in the major German weekly newspapers (Bild, FAZ, Spiegel, SZ, taz, Welt), 2014-2017."}
 
@@
 In order to identify different considerations in media coverage, I will use a two-step approach.
-After training a neural network (BERT) to classify migration content in news coverage (providing a measure of salience), I employ the structural topic model[^2] [@Roberts2019], to identify different topics being raised *within* migration coverage.
-This model allows to specify covariates, such as different prevalence of frames across newspapers.
-The topic model might for example identify topics like crime, terrorism, refugee deaths, and the distribution of refugees.
+After training a neural network (BERT) to classify migration content in news coverage (providing a measure of salience), I employ the structural topic model[^3] [@Roberts2019], to identify different topics being raised *within* migration coverage.
+This model allows to specify covariates, such as different prevalence of frames across newspapers, to model the distribution of topics.
+The model might for example identify topics like crime, terrorism, refugee deaths, and the distribution of refugees.
 Each of these topics represents a consideration about migration, which will have implications for the evaluation of the issue.
 
-[^2]: At this point, I am not sure if I might not instead use a simple LDA.
+[^3]: At this point, I am not sure if I might not instead use a simple LDA.
 
@@
 To measure the emphasis of different considerations in party communication, I select all paragraphs from parties' election manifestos in the 2017 election that are concerned with migration.
-For each party, I generate a topic vector using the model described in section, based on the collection of all relevant paragraphs \@ref(measuring-migration-framing-in-the-media).
+For each party, I generate a topic vector using the model described in section \@ref(measuring-migration-framing-in-the-media), based on the collection of all relevant paragraphs.
 
-Now, using these party-framing vectors, *I can assess the similarity of each news article towards each party's migration framing, simply by taking the cosine distance to the party's vector*.
-Figure \@ref(fig:vectors) gives a two-dimensional example: the article vector (representing the distribution of different considerations within the article) is clearly closer to the vector of party a (representing the distribution of considerations in party a's communication), compared to party b.
+Now, using these party-frame vectors, *I can assess the similarity of each news article towards each party's migration framing, simply by taking the cosine distance to the party's vector*.
+Figure \@ref(fig:vectors) gives a two-dimensional example: Each axis indicates the relative attention to a single consideration of the immigration issue.
+The article vector (representing the distribution of different considerations within the article) is clearly closer to the vector of party a (representing the distribution of considerations in party a's communication), compared to party b.
 
@@
 
-```{r vectors}
+```{r vectors, fig.cap="Schematic representation of topic vectors for party communication and news articles."}
 
@@
 
-As the above approach will provide me with time-series data on the similarity of the public debate surrounding migration to each parties' definition of migration, and given the time-series structure of the polling data (the dependent variable), it seems straightforward to use time-series modeling, and specifically vector-auto-regression (VAR) models[^3] [@Sims1980] to account for possible effects of the polls on media reporting about migration.
+As the above approach will provide me with time-series data on the similarity of the public debate surrounding migration to each parties' definition of migration, and given the time-series structure of the polling data (the dependent variable), it seems straightforward to use time-series modeling, and specifically vector-auto-regression (VAR) models[^4] [@Sims1980] to account for possible effects of the polls on media reporting about migration.
 
-[^3]: As I never used VAR models to model interaction effects, I am not entirely sure how to account for variation in salience here.
+[^4]: As I never used VAR models to model interaction effects, I am not entirely sure how to account for variation in salience here.
 It might still be possible to use split samples of periods with higher and lower salience, or restrict the analysis to a period with relatively stable attention to migration (e.g.
@@
 
-An additional possibility in order to improve causal identification was to use exogenous events like the new years eve in cologne, terrorist attacks abroad or drownings in the Mediterranean sea to instrument attention to specific topics.
-This idea has not far progressed, so I am curious about your thoughts on this.
+An additional possibility in order to improve causal identification and address endogeneity issues were to use unexpected exogenous events like the new years eve in cologne, terrorist attacks abroad or drownings in the Mediterranean sea to instrument attention to specific topics.
+The idea would be that these must be events that cannot be affected by polls (so e.g.
+radical-right attacks would likely not work) and vice versa do not affect polls through any other mechanism but media attention.
+Using two-stage least-squares regression (2SLS), I predict coverage of certain topics and use the predicted values as the main independent variable in the VAR model.
+As my thinking on this has not progressed much yet, I am curious about your thoughts.
 

### 2022-07-10 pres/Presentation.Rmd
Add svg image to presentation and Readme

---
title: "Frame Competition"
subtitle: "How News Framing affects Party Competition"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    seal: false
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: true
      ratio: 16:9
    includes:
      after_body: insert-logo.html
---

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#004A95", background_color = "#bfbfbf",
  base_font_size = "32px",
  header_h1_font_size = "1.3rem",
  header_h2_font_size = "1.2rem",
  header_h3_font_size = "1.05rem",
  footnote_font_size = "0.75rem",
  header_font_google = google_font("Lato", '700'),
  text_font_google   = google_font("Lato", "400"),
  code_font_google   = google_font("Fira Mono")
)

```

```{r, load_refs, include=FALSE, cache=FALSE}
library(RefManageR)
BibOptions(check.entries = FALSE, 
           bib.style = "authoryear",
           cite.style = "authoryear",
           style = "markdown",
           hyperlink = FALSE,
           max.names = 2, 
           longnamesfirst = F,
           dashed = FALSE)
myBib <- ReadBib("C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib", check = FALSE)
```

```{r setup, include=FALSE}

knitr::opts_chunk$set(
  echo = FALSE, 
  message = F, 
  warning = F, 
  cache = T, 
  out.width="90%", 
  fig.height=8, 
  fig.width=15, 
  fig.align='center', 
  eval = T, 
  dev = "svg"
  )
# knitr::opts_knit$set(root.dir = 'C:/Users/nicol/Dropbox/PhD/Papers/Bild/github/bild')

library(tidyverse)
library(dplyr)
library(data.table)
library(fixest)
library(lubridate)
library(patchwork)
library(here)

# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}

```

```{r vectors, fig.cap="Schematic representation of topic vectors for party communication and news articles."}

data.frame(
  item = c("News Article", "Party A", "Party B",
            "News Article", "Party A", "Party B"),
  dim1 = c(0,  0.2, 0.8,
            0,0,0),
  dim2 = c(1, 0.8, 0.2,
            0,0,0)
) %>% 
ggplot(aes(x = dim1, y = dim2, 
        color = item, linetype = item)) +
  geom_line() +
  geom_point(alpha = 0.3) + 
  theme_minimal() +
  xlab("Attention to Consideration 1") +
  ylab("Attention to Consideration 2") +
  theme(legend.title = element_blank())

```

### 2022-07-12 pres/Presentation.Rmd
Update image
start presentation

@@
   base_color = "#004A95", background_color = "#bfbfbf",
-  base_font_size = "32px",
+  base_font_size = "40px",
   header_h1_font_size = "1.3rem",
   header_h2_font_size = "1.2rem",
-  header_h3_font_size = "1.05rem",
+  header_h3_font_size = "1rem",
   footnote_font_size = "0.75rem",
@@
 
-```{r vectors, fig.cap="Schematic representation of topic vectors for party communication and news articles."}
+class: inverse, center, middle
+
+# Frame Competition
+
+#### Nicolai Berk<sup>*</sup>
+
+Presentation prepared for the first OX|BER Graduate Workshop
+
+Berlin, 14th of July
+
+.left[.footnote[<sup>*</sup> Dynamics RTG & Humboldt Universität Berlin]]
+
+---
+
+## Motivation: Issue Ownership
+
+```{r MPAtt}
+
+fread("https://www.dropbox.com/s/3taauo34rumthtm/final_dataset.csv?dl=1") %>% 
+  mutate(date = as.Date(date, format = "%d/%m/%Y"),
+         month = lubridate::floor_date(date, "quarter")) %>% 
+  filter(date >= as.Date("2013-01-01")) %>% 
+  group_by(month, sender) %>% 
+  summarise(imm_att = mean(coding)) %>% 
+  ggplot(aes(month, imm_att, fill = sender)) +
+  geom_col(position = "dodge2") + 
+  theme_minimal() +
+  ggtitle("Attention to migration in mainstream parties' press releases", "2013-2019") +
+  scale_fill_manual(values = c("#000000", "#e3000f")) +
+  theme_xaringan() +
+  ylab("") + xlab("")
+
+```
+
+---
+
+## Motivation II
+
+- Parties only option to **remain mute** on other parties' issues?
+- Framing literature suggests that issue definitions affect voters' policy preferences.
+- Some experimental literature that this can affect issue ownership [@Seeberg2019].
+
+--
+
+### But can framing affect voting behaviour?
+
+---
+
+## Argument
+
+1. Issue framing affects issue preferences.
+2. Dominant framing of an issue changes public opinion on that issue.
+3. Public votes based on proximity to parties' issue positions.
+
+### Issues more or less beneficial dependent on *dominant framing*!
+
+---
+
+class: center, inverse, middle
+
+# Research Design
+
+---
+
+---
+
+## Measuring Frame Dominance
+
+```{r vectors}
 
@@
         color = item, linetype = item)) +
-  geom_line() +
-  geom_point(alpha = 0.3) + 
+  geom_line(size = 2) +
+  geom_point(alpha = 0.3, size = 4) + 
   theme_minimal() +
@@
   ylab("Attention to Consideration 2") +
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank()) +
+  theme_xaringan()
 

### 2022-07-13 pres/Presentation.Rmd
Finish slides for OX|BER

@@
       highlightLines: true
-      countIncrementalSlides: true
+      countIncrementalSlides: false
       ratio: 16:9
@@
 
-## Motivation: Issue Ownership
+## Issue Ownership Theory
+
+```{r IssueOwnership}
+
+data.frame(
+  Party = c("A", "A", "B", "B"),
+  Issue = c("A's", "B's", "A's", "B's"),
+  Votes = c(0.3, 0.1, 0.1, 0.3)
+) %>% 
+  ggplot(aes(Issue, Votes, col = Party)) +
+  geom_point(size = 4) +
+  geom_line(aes(group = Party), size = 2) +
+  theme_xaringan() +
+  xlab("Salient Issue")
+
+```
+
+---
+
+## Parties behave accordingly
 
@@
 
-## Motivation II
+## Research Question
 
@@
 - Framing literature suggests that issue definitions affect voters' policy preferences.
-- Some experimental literature that this can affect issue ownership [@Seeberg2019].
+- Experimental work shows that framing can affect issue ownership (Seeberg 2019).
 
@@
 
-### But can framing affect voting behaviour?
+### Does framing affect voting behaviour?
 
@@
 
+class: inverse
+
 ## Argument
 
-1. Issue framing affects issue preferences.
-2. Dominant framing of an issue changes public opinion on that issue.
-3. Public votes based on proximity to parties' issue positions.
+<br>
 
-### Issues more or less beneficial dependent on *dominant framing*!
+### 1. Issue framing affects issue attitudes.
+### 2. Dominant media framing changes public opinion.
+### 3. Policy preferences translate into voting behaviour.
+
+--
+
+## Media Framing $\rightarrow$ Voting Behaviour
 
@@
 
-class: center, inverse, middle
+## Research Design
 
-# Research Design
+<br>
+
+### 1. Measure similarity of media framing to party framing.
+### 2. Estimate effect of similarity on electoral performance.
 
@@
 
+## Data
+
+### Media Content
+
+Collected **2.5M news articles** from major German newspapers' websites (2013-2019).
+
+.pull-left[
+
+### (Expected) Electoral Performance
+
+]
+
+.pull-right[
+
+  ![](https://www.politico.eu/wp-content/uploads/2022/02/01/Poll-of-Polls.svg)
+
+]
+
+- Polling data collected by *Politico's [Poll of Polls](https://www.politico.eu/europe-poll-of-polls/)*.
+- Generates daily moving average of party support.
+
 ---
 
-## Measuring Frame Dominance
+## Data II
 
-```{r vectors}
+<br>
+
+### Party framing
+
+- 2017 Manifesto corpora, reduced to migration content.
+- Ideal because **summarise general position** on the issue.
+- Downside: assumption of stable position over time.
+
+---
+
+## Measuring Issue Framing
+
+.pull-left[
+
+  ![](vis/CognitiveStorage.png)
+
+]
+
+.pull-right[
+
+1. Identify media content relating to issue:
+  - Annotate sample
+  - Supervised ML (BERT)
+2. Identify considerations:
+  -  Topic model
+
+]
+
+---
+
+## Measuring Frame Similarity
+
+```{r vectors, fig.height=7, cache=FALSE}
 
@@
 ```
+
+---
+
+## Measuring Frame Similarity
+
+### Why frame *similarity*?
+
+- Parties communicate a certain framing either as cause or outcome of their positions.
+- If media framing is **similar**, this supports a parties' position.
+- As a result, citizens are more likely to vote for party.
+
+--
+
+### Measurement
+
+$$Similarity_{Party, t} = cos(TopicVector_{Media}, TopicVector_{Party})_t$$
+
+---
+
+## SVAR Time Series Model
+
+<br>
+
+- VAR allows modeling multiple time series as functions of own and other variables past.
+- Structural VAR allows modeling interaction $Performance = Salience*Similarity$.
+- Estimate of interest: effect of similarity on electoral performance.
+
+---
+
+## Instrumental Variable Approach
+
+.left-column[
+
+```{r dagInstrument, fig.align='center'}
+DiagrammeR::grViz("
+digraph boxes_and_circles {
+
+  rankdir = 'TB'
+  bgcolor = '#bfbfbf'
+
+  # a 'graph' statement
+  graph [overlap = true, 
+          fontsize = 16]
+
+  # several 'node' statements
+  node [shape = plaintext,
+        fontname = Verdana,
+        fontcolor = black]
+  Z [label = 'Events', fontcolor = '#004A95']
+  X [label = 'Media Framing']
+  Y [label = 'Voting']
+
+  # several 'edge' statements
+  Z->X [color = '#004A95']
+  X->Y [color = black]
+}
+")
+
+```
+
+]
+
+.right-column[
+
+Events drive media attention to considerations, e.g.
+
+- Migrant crime,
+- Terrorist Attacks,
+- Drownings.
+
+### These should only affect public opinion through media coverage.
+
+]
+
+---
+
+## Instrumental Variable Approach II
+
+<br>
+
+- Framing can be instrumented using exogenous events.
+- Predicted frame attention can then be used to estimate causal effect (**2SLS**).
+
+---
+
+## Summary
+
+<br>
+
+- **Goal**: Project tries to challenge assumption that issues always affect voters similarly.
+- **Argument**: dominant media framing of issues affects party support.
+- **Methods**: 
+  + innovative measure of frame similarity,
+  + combination of time-series and causal inference tools (SVAR + IV).
+
+---
+
+## Open Questions
+
+- Does theory make sense?
+- Time Frame (2017 campaign or longer?)
+- Manifestos for party frames?
+- SVAR correct model? (might go for unidirectional model with 2SLS)
+- Additional Experiment?
+- ...?
+
+---
+
+class: inverse, middle, center
+
+# Fin
+
+## Thank you!
+
+.pull-left[![](vis/banner_new.png)]
+
+.pull-right[![](vis/dfg_logo_englisch_blau_en.jpg)]

### 2022-07-13 pres/Presentation.Rmd
Update pres, add pdf

@@
       highlightLines: true
-      countIncrementalSlides: false
+      countIncrementalSlides: true
       ratio: 16:9
@@
   warning = F, 
-  cache = T, 
+  cache = F, 
   out.width="90%", 
@@
 
-<br>
-
 ### 1. Issue framing affects issue attitudes.
@@
 ### 3. Policy preferences translate into voting behaviour.
+
+<br>
 
@@
 
-$$Similarity_{Party, t} = cos(TopicVector_{Media}, TopicVector_{Party})_t$$
+$$Similarity_{p, t} = cos(TopicVector_{Media}, TopicVector_{p})_t$$
 
@@
 
-<br>
-
 - **Goal**: Project tries to challenge assumption that issues always affect voters similarly.

### 2022-12-08 paper/Manuscript.Rmd
Add plots
Preliminary Analyses, update Abstract

@@
 ---
-title: "Frame Competition"
+title: "Frame Competition - Assessing the Impact of News Framing on Parties' Electoral Performance with Document Embeddings"
 author: "Nicolai Berk"
@@
 abstract: "Issue ownership theory assumes that the salience of specific issues is always more or less beneficial to a given party.
-I introduce the concept of 'frame competition' and argue that a given issue can be more or less beneficial for parties dependent on the dominant framing.
-I test this argument using data from the German 2017 Bundestag campaign, assessing the similarity of media coverage on migration to parties' migration framing with topic vectors.
-Using VAR models and an instrumental variable approach, I show whether higher frame similarity is associated with better performance in the polls.
-The findings broaden our understanding party competition and underline possibilities for political change, as well as parties' capability to compete, even when the issue agenda is given."
+I introduce the concept of frame competition and argue that a given issue can be more or less beneficial for parties, dependent on the dominant framing.
+I test this argument by estimating the similarity of media coverage about migration to parties' migration framing with document embeddings, using data from Germany 2013-2019.
+Combining this similarity measure with VAR models, I show whether higher frame similarity is associated with better performance in the polls.
+The findings broaden our understanding of voting behaviour and the strategies political parties can employ in the face of a hostile issue agenda."
 bibliography: C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib
@@
 
-knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.height=6, fig.width=10, fig.align='center', eval = T)
+knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T)
 
@@
 
+*This manuscript has been enriched by commentary from Tarik Abou-Chadi, Daniel Bischof, Luis Cornago Bonal, Sophia Hunger, Antonio Valentim, Klaudia Wegschaider, Lisa Zehnter.*
+
 # Introduction
@@
 One of the most prominent explanations for parties' electoral success in scholarly and public debate is the issue agenda at a given election: the more prominent an issue was among political parties, news media, and voters, the more it would influence the latter's electoral decision making.
-Certain issues are therefor more favorable to given parties and parties will try to focus on 'their' issues in public communication [@Budge1983; @Petrocik1996; @Walgrave2012].
+Certain issues are therefore more favorable to given parties and parties will try to focus on 'their' issues in public communication [@Budge1983; @Petrocik1996; @Walgrave2012].
 In extension, it is assumed that the main form of electoral competition in contemporary Western European democracies is *issue competition*, in the sense that parties compete to bring 'their' issue on the agenda [@GreenPedersen2019].
@@
 
+<!-- Sophia Hunger: does associative framing really affect voting? [I am not sure if it is so relevant to go into this distinction] -->
+
 Whichever the mechanism, both conceptualizations imply that parties perform better electorally when 'their' issue is on the top of the agenda, because voters either are more likely to perceive them as the most competent party in the current issue environment or because they are simply more likely to make it to the pool of viable options in a voters' mind:
@@
 migrants dying at the border, or refugees fleeing war, the issue should favor those parties with more welcoming migration positions more compared to when migration is discussed as a security problem, emphasizing crime and the potential danger of terrorism.
+
+<!-- Sophia HUnger finds the above paragraph very convincing ;) -->
 
@@
   mutate(week = lubridate::floor_date(date, "week")
-         # , post = date >= as.Date("2016-01-01")
+         , post = date >= as.Date("2016-01-01")
          ) %>% 
   group_by(week
-           # , post
+           , post
            ) %>% 
@@
   ggplot(aes(week, parties.AfD
-             # , group = post
+             , group = post
              )) +
@@
 As we can see, the increase in voting intention for the radical right party trails the increase in salience by several months.
-In fact, the party experiences a \*low\* right around the peak in immigration coverage.
+In fact, the party experiences a *low* right around the peak in immigration coverage.
 Why might that be?
@@
 Especially new years eve 2015/16 marked a turning point, when hundreds of sexual abuses by men whom the victims perceived to be of arabic descent in Cologne were reported (if you look closely, you can see a discontinuity surrounding that date in the AfD-share, which increases around one and a half percentage points at that very date).
+
+<!-- Sophia Hunger likes this -->
 
@@
 One key difference compared to other models of party competition, especially the one described in @Meguid2005 is that in the present model, party positions are considered fixed, while it is the media debate that moves.
-Large shifts in parties' issue positions are generally rare [@SOURCE], but the media debate is in permanent flux, promoting a constantly changing set of issues and related considerations to voters.
+Large shifts in parties' issue positions are generally rare [@Gessler2022], but the media debate is in permanent flux, promoting a constantly changing set of issues and related considerations to voters.
 Political actors sponsor frames and arguments, only some of which get to influence the debate.
@@
 After the refugee movements throughout Europe in 2015, voters considered migration the most important issue [@Wessels2021, p.
-12], and the media still discussed the issue, but at lower levels compared to 2017 (see figure \@ref(fig:salplot)).
+12], and the media still discussed the issue, but at lower levels compared to 2015 (see figure \@ref(fig:salplot)).
 I expect that events during the election campaign, such as migrant crimes, conflicts regarding the intra-EU distribution of refugees, international terrorism, humanitarian crises as those among the Rohingya in Myanmar, as well as drownings in the Mediterranean sea lead to substantial variation in the set of considerations regarding migration being discussed - the key independent variable.

### 2022-12-08 paper/explore/ExplorationFrames.qmd
Preliminary Analyses, update Abstract

---
title: "Preliminary Analysis Party Frames Migration"
author: "Nicolai Berk"
format: html
editor: visual
---

## Introduction

```{r setup}

knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = T, fig.height=6, fig.width=10, fig.align='center', eval = T)

# Setup ####
library(tidyverse)
library(here)
library(data.table)
library(word2vec)

# load self-made functions
for (filename in list.files(here("code/functions"))){
  source(here(paste0('code/functions/', filename)))
}

```

This document contains some preliminary analyses of frames employed in news coverage and party communication about migration. All analyses are based on a subsample and supposed to inform any analyses on a broader sample later on.

## Explore Embeddings

We start by exploring the quality of our word embeddings:

```{r wordembeddings}

# load model
w2v_model <- 
  read.word2vec(here("data/processed/embeddings/w2v_news_sample.bin"))

# read vectors
load(here("data/processed/embeddings/w2v_news_vectors_sample.Rdata"))

vector <- emb["Ausländer", ]
predict(w2v_model, vector, type = "nearest", top_n = 10)

```

## Frames in Migration coverage

## Frames in Party Coverage

## Association of Party and Migration Coverage

### 2022-12-08 code/embeddings/party_embeddings.R

@@ -1,0 +1,33 @@
+# ______________________________________________
+# FrameCompetition
+# Goal: Estimate Party Embeddings
+# Procedure: get manifestos, embed, save
+# ______________________________________________
+# Date:  Tue Nov 29 14:53:44 2022
+# Author: Nicolai Berk
+#  R version 4.1.1 (2021-08-10)
+# ______________________________________________
+
+
+whitelist <- ls()
+
+## load party manifestos on migration (2013)
+partycom <- fread(here("data/media/migcov_sample.csv"), encoding = "UTF-8")
+
+## load word embeddings trained on full set
+
+emb <- read.word2vec("newsembeddings")
+
+
+## generate document embeddings
+doc2vec(w2v_model, party_com)
+
+# embed ####
+d2v_model <- doc2vec(
+  read.word2vec("data/processed/embeddings/w2v_news.bin"),
+  "data/raw/migration_manifestos/")
+
+# save ####
+
+# clean up
+rm(ls()[!ls() %in% whitelist])

### 2022-12-08 code/embeddings/word_embeddings.R

@@ -9,13 +9,32 @@
 # ______________________________________________
 
 
+whitelist <- ls()
+
 # estimate embeddings ####
-w2v_model <- word2vec(paste0("data/processed/media/news_merged",
-                             ifelse(sampling, "_sample", ""),
-                             ".csv"), 
-                      dim = 300, window = 5, iter = 20, 
-                      min_count = 100, threads = 6)
+w2v_model <- word2vec(
+  fread(
+    here(
+      paste0("data/processed/media/news_merged",
+             ifelse(sampling, "_sample", ""),
+             ".csv")
+      ), 
+    encoding = "UTF-8")$text, 
+  dim = 300, window = 5, iter = 20, 
+  min_count = 100, threads = 6)
 
 # save ####
 word2vec::write.word2vec(w2v_model, 
-                         "data/processed/embeddings/w2v_news.bin")
+                         paste0("data/processed/embeddings/w2v_news",
+                                ifelse(sampling, "_sample", ""),
+                                ".bin"))
+
+emb <- as.matrix(w2v_model)
+
+save(emb,
+     file = paste0("data/processed/embeddings/w2v_news_vectors",
+                   ifelse(sampling, "_sample", ""),
+                   ".Rdata"))
+
+rm(ls()[!ls() %in% whitelist])
+

### 2022-12-08 code/main.R

@@ -15,7 +15,7 @@ library(word2vec)
 library(manifestoR)
 
 # parameters ####
-sampling <- T
+sampling <- F
 
 # cleaning ####
 cat("Cleaning in progress...")
@@ -44,7 +44,7 @@ cat("Done sampling.\n\n")
 # embeddings ####
 cat("Estimating embeddings...")
 
-cat("\tEstimating word2vec...")
+cat("\tEstimating word2vec (be patient) ...")
 source("code/embeddings/word_embeddings.R")
 
 cat("\tEstimating doc2vec: party embeddings...")

### 2022-12-08 code/preprocessing/get_manifestos.R

@@ -9,16 +9,18 @@
 # ______________________________________________
 
 # parameters ####
-clean_list <- c()
+whitelist <- ls()
 
 
 # Get data ####
 mp_setapikey("data/raw/manifestos/manifesto_apikey.txt")
 
-my_corpus <- mp_corpus(countryname == "Germany" & edate > as.Date("2020-01-01"))
+my_corpus <- mp_corpus(countryname == "Germany" & 
+                         edate < as.Date("2014-01-01") & 
+                         edate > as.Date("2013-01-01"))
 
 #
-mpds <- mp_maindataset()
+mpds <- mp_maindataset(); clean_list <- c(clean_list, "mpds")
 
 # generatae dataset ####
 corpus <- data.frame(doc_id = NULL, text = NULL)
@@ -44,8 +46,5 @@ for (doc in names(my_corpus)){
 fwrite(corpus, "data/raw/manifestos/manifestos.csv")
 
 # clean up ####
-rm(list = clean_list)
-
-
-
+rm(ls()[!ls() %in% whitelist])
 

### 2022-12-08 code/preprocessing/news_sampling.R

@@ -13,7 +13,3 @@ fread("data/processed/media/news_merged.csv") %>%
   sample_n(10000) %>% 
   fwrite("data/processed/media/news_merged_sample.csv")
 
-fread("data/processed/media/news_merged_textonly.txt") %>% 
-  sample_n(10000) %>% 
-  fwrite("data/processed/media/news_merged_textonly_sample.txt")
-

### 2022-12-08 code/preprocessing/preprocess_news.R

@@ -10,7 +10,9 @@
 
 clean_list <- c()
 
-for (corpus in list.files(here("data/raw/media/newspapers"))){; clean_list <- c(clean_list, "corpus")
+clean_list <- c(clean_list, c("corpus", "dta"))
+
+for (corpus in list.files(here("data/raw/media/newspapers"))){
   
   if (str_detect(corpus, "bild")){
     
@@ -71,17 +73,11 @@ for (corpus in list.files(here("data/raw/media/newspapers"))){; clean_list <- c(
            append = T, 
            showProgress = T)
     
-    fwrite(dta$text,
-           file = "data/processed/media/news_merged_textonly.csv", 
-           append = T)
-    
   }else{
     
     fwrite(dta,
-           file = "data/processed/media/news_merged.csv")
-    
-    write(list(dta$text),
-           file = "data/processed/media/csv")
+           file = "data/processed/media/news_merged.csv", 
+           showProgress = T)
     
   }
   

### 2023-04-14 paper/Manuscript.Rmd
update intro, adding document embeddings

@@
 
-*This manuscript has been enriched by commentary from Tarik Abou-Chadi, Daniel Bischof, Luis Cornago Bonal, Sophia Hunger, Antonio Valentim, Klaudia Wegschaider, Lisa Zehnter.*
+*This manuscript has been enriched by commentary from Tarik Abou-Chadi, Daniel Bischof, Luis Cornago Bonal, Sophia Hunger, Thomas Meyer, Antonio Valentim, Klaudia Wegschaider, and Lisa Zehnter.*
 
@@
 
-The present paper sets out to challenge this simple model of issue ownership by looking into party competition *within* issues.
+The present paper sets out to challenge this simple model of issue ownership by looking into party competition *within* issues - specifically, the migration issue.
 Building on a large body of experimental work, I argue that - dependent on the relative emphasis of different considerations in public debate, also known as *emphasis framing* - any issue can be more or less favorable to a given party.
@@
 
-I test this argument using data from the German 2017 Bundestag campaign, during which the immigration issue - which became salient after the 2015 refugee movements - dominated public debate in the media and among parties, as well as voters' perception of the most important problems in national politics.
-Using topic representations of media content and parties' manifestos as an anchor point, I track the similarity of the migration discourse in national newspapers to parties' communication about migration.
+I test this argument using data from German newspapers 2013-2019.
+During the first half of this period leading up to the lower house election 2017, the immigration issue - which became salient after the 2015 refugee movements - dominated public debate in the media and among parties, as well as voters' perception of the most important problems in national politics.
+Using vector representations of media content and parties' manifestos (so-called document embeddings), I track the similarity of the migration discourse in national newspapers to parties' communication about migration.
 Combining these daily similarity estimates with polling data from *Poll of Polls*[^1] using vector auto-regression (VAR) models [@Sims1980] and an instrumental variable approach, I assess whether parties' electoral prospects increase when the media discourse is more similar to a given party's representation of the migration issue.

### 2023-04-14 paper/Manuscript.Rmd
make design consistent

@@
 
-I test this argument using data from German newspapers 2013-2019.
-During the first half of this period leading up to the lower house election 2017, the immigration issue - which became salient after the 2015 refugee movements - dominated public debate in the media and among parties, as well as voters' perception of the most important problems in national politics.
+I test this argument using data from the German 2017 Bundestag campaign, during which the immigration issue - which became salient after the 2015 refugee movements - dominated public debate in the media and among parties, as well as voters' perception of the most important problems in national politics.
 Using vector representations of media content and parties' manifestos (so-called document embeddings), I track the similarity of the migration discourse in national newspapers to parties' communication about migration.

### 2023-04-14 code/embeddings/party_embeddings.R
switch to integrated estimation of doc and top vec

@@ -1,33 +1,0 @@
-# ______________________________________________
-# FrameCompetition
-# Goal: Estimate Party Embeddings
-# Procedure: get manifestos, embed, save
-# ______________________________________________
-# Date:  Tue Nov 29 14:53:44 2022
-# Author: Nicolai Berk
-#  R version 4.1.1 (2021-08-10)
-# ______________________________________________
-
-
-whitelist <- ls()
-
-## load party manifestos on migration (2013)
-partycom <- fread(here("data/media/migcov_sample.csv"), encoding = "UTF-8")
-
-## load word embeddings trained on full set
-
-emb <- read.word2vec("newsembeddings")
-
-
-## generate document embeddings
-doc2vec(w2v_model, party_com)
-
-# embed ####
-d2v_model <- doc2vec(
-  read.word2vec("data/processed/embeddings/w2v_news.bin"),
-  "data/raw/migration_manifestos/")
-
-# save ####
-
-# clean up
-rm(ls()[!ls() %in% whitelist])

### 2023-04-14 code/embeddings/word_embeddings.R

@@ -1,40 +1,0 @@
-# ______________________________________________
-# Media Frames and Party Competition
-# Goal: Estimate word embeddings
-# Procedure: estimate embeddings, save
-# ______________________________________________
-# Date:  Tue Nov 29 14:11:58 2022
-# Author: Nicolai Berk
-#  R version 4.1.1 (2021-08-10)
-# ______________________________________________
-
-
-whitelist <- ls()
-
-# estimate embeddings ####
-w2v_model <- word2vec(
-  fread(
-    here(
-      paste0("data/processed/media/news_merged",
-             ifelse(sampling, "_sample", ""),
-             ".csv")
-      ), 
-    encoding = "UTF-8")$text, 
-  dim = 300, window = 5, iter = 20, 
-  min_count = 100, threads = 6)
-
-# save ####
-word2vec::write.word2vec(w2v_model, 
-                         paste0("data/processed/embeddings/w2v_news",
-                                ifelse(sampling, "_sample", ""),
-                                ".bin"))
-
-emb <- as.matrix(w2v_model)
-
-save(emb,
-     file = paste0("data/processed/embeddings/w2v_news_vectors",
-                   ifelse(sampling, "_sample", ""),
-                   ".Rdata"))
-
-rm(ls()[!ls() %in% whitelist])
-

### 2023-04-14 code/main.R

@@ -1,56 +1,0 @@
-# ______________________________________________
-# Media Frames and Party Competition
-# Main Execution FIle
-# ______________________________________________
-# Date:  Tue Nov 29 14:06:58 2022
-# Author: Nicolai Berk
-#  R version 4.1.1 (2021-08-10)
-# ______________________________________________
-
-# Setup ####
-library(tidyverse)
-library(here)
-library(data.table)
-library(word2vec)
-library(manifestoR)
-
-# parameters ####
-sampling <- F
-
-# cleaning ####
-cat("Cleaning in progress...")
-
-cat("\tClean and merge news corpus...")
-source("code/preprocessing/preprocess_news.R")
-
-cat("\tget manifestos...")
-source("code/preprocessing/get_manifestos.R")
-
-
-cat("All cleaned up.\n\n")
-
-
-
-# sampling ####
-cat("Sampling...")
-if(sampling){
-  cat("\tSampling from news corpus...")
-  source("code/preprocessing/news_sampling.R")
-}
-cat("Done sampling.\n\n")
-
-
-
-# embeddings ####
-cat("Estimating embeddings...")
-
-cat("\tEstimating word2vec (be patient) ...")
-source("code/embeddings/word_embeddings.R")
-
-cat("\tEstimating doc2vec: party embeddings...")
-source("code/embeddings/party_embeddings.R")
-
-cat("\tEstimating doc2vec: ...")
-source("code/embeddings/news_embeddings.R")
-
-cat("Estimation of embeddings finished.\n\n")

### 2023-04-14 code/collection/polls.R
Collect polls

@@ -1,0 +1,38 @@
+## setup
+library(tidyverse)
+library(jsonlite)
+
+## read data
+polls_json <- fromJSON("https://www.politico.eu/wp-json/politico/v1/poll-of-polls/DE-parliament")
+
+
+
+## clean
+polls_tidy <- 
+    polls_json$polls %>%
+    flatten() %>%
+    as_tibble() %>%
+    pivot_longer(cols = -c(date, firm, date_from, sample_size), 
+    names_to = "party",
+    names_prefix = "parties.", 
+    values_to = "value") %>%
+    mutate(date = as.Date(date))
+
+## plot
+plt <- polls_tidy %>%
+    ggplot(aes(x = date, y = value, color = party)) +
+    geom_point(alpha = 0.025) +
+    geom_smooth() +
+    facet_wrap(~party) +
+    scale_color_manual(values = 
+                        c("lightblue", "yellow", "green",
+                        "purple", "orange", "red", "blue")) +
+    theme_minimal()
+
+png("plots/polls.png", width = 10, height = 8, units = "in", res = 300)
+plt
+dev.off()
+
+## save
+polls_tidy %>% 
+    write_csv("data/processed/polls.csv")

### 2023-04-14 code/estimation/var.r
Estimate Poll-Topic VAR

@@ -1,0 +1,86 @@
+# run var for all party-topic combinations
+
+## setup
+library(tidyverse)
+library(vars)
+source("code/functions/var_topic.r")
+# source("code/functions/var_prep.r")
+
+## load parties and topics
+merged <- data.table::fread("data/processed/media/merged.csv")
+
+parties <- 
+    merged %>% 
+    dplyr::select(AfD:Union) %>% 
+    dplyr::select(-PIRATEN) %>%
+    colnames()
+
+topics <-
+    merged %>% 
+    dplyr::select(contains("Association")) %>% 
+    dplyr::select(!contains("Stock Market")) %>%
+    colnames() %>%
+    str_replace("Association \\(reduced\\): ", "") %>%
+    str_replace("Association ", "")
+
+rm(merged)
+
+## run var for all party-topic combinations
+var_results <-
+    expand.grid(
+
+        ## inputs
+        topic = topics,
+        party = parties,
+        controls = NA,
+        aggregation = c("yw", "ym", "yq"),
+        topic_metric = c("association", "share", "absolute"),
+        
+        ## outputs
+        point_party_dv = NA,
+        lower_party_dv = NA,
+        upper_party_dv = NA,
+        
+        point_topic_dv = NA,
+        lower_topic_dv = NA,
+        upper_topic_dv = NA,
+
+        stringsAsFactors = F
+    ) %>%
+    mutate(
+        lag_max =
+            case_when(
+                aggregation == "yw" ~ 12,
+                aggregation == "ym" ~ 12,
+                aggregation == "yq" ~ 4,
+                aggregation == "date" ~ 30
+            )
+    )
+
+for (i in seq_len(nrow(var_results))) {
+
+    print(paste(i, "/", nrow(var_results)))
+
+
+
+    var_raw <-
+        var_topic(
+            party = var_results$party[i],
+            topic = var_results$topic[i],
+            aggregation = var_results$aggregation[i],
+            topic_metric = var_results$topic_metric[i],
+            controls = var_results$controls[i],
+            max_lag = var_results$lag_max[i],
+            plot_var = FALSE
+        )
+
+    var_results[i, c("point_party_dv", "lower_party_dv", "upper_party_dv")] <-
+        var_raw$`poll ~ topic`
+
+    var_results[i, c("point_topic_dv", "lower_topic_dv", "upper_topic_dv")] <-
+        var_raw$`topic ~ poll`
+}
+
+
+## save results
+write.csv(var_results, "data/processed/estimation/var_results.csv", row.names = F)

### 2023-04-14 code/estimation/var_vis.r

@@ -1,0 +1,284 @@
+library(tidyverse)
+library(dplyr)
+
+## load data
+var_results <- read.csv("data/processed/estimation/var_results.csv")
+
+## topics
+merged <- data.table::fread("data/processed/media/merged.csv")
+merged %>%
+    dplyr::select(`AfD Topic`:`Young Refugees`) %>%
+    summarise_all(sum) %>%
+    t() -> topic_dist
+
+row.names(topic_dist)[order(topic_dist, decreasing = T)] -> top_topics
+
+top_topics <- c(top_topics, "AfD Topic")
+
+## plot
+var_results %>%
+    filter(topic_metric == "association",
+           aggregation == "yw",
+           topic %in% top_topics,
+           is.na(controls)) %>%
+    ggplot(aes(y = topic,
+               x = point_party_dv, 
+               xmin = lower_party_dv,
+               xmax = upper_party_dv,
+               color = (lower_party_dv > 0 | upper_party_dv < 0))) +
+    geom_vline(xintercept = 0) +
+    geom_pointrange() +
+    theme_minimal() +
+    theme(legend.position = "none") +
+    facet_grid(~party, scales = "free_x") +
+    ggtitle("Framing Effects on Party Polling")
+
+ggsave(filename = "plots/var_top_topics.svg", width = 15, height = 10)
+
+
+## plot all estimates sorted by effect size per party
+for (p in unique(var_results$party)){
+    var_results %>%
+        filter(topic_metric == "association",
+               aggregation == "yw",
+               is.na(controls),
+               party == p) %>%
+        ggplot(aes(x = reorder(topic, -point_party_dv),
+                   y = point_party_dv, 
+                   ymin = lower_party_dv,
+                   ymax = upper_party_dv,
+                   color = (lower_party_dv > 0 | upper_party_dv < 0))) +
+        geom_hline(yintercept = 0) +
+        geom_pointrange() +
+        theme_minimal() +
+        theme(
+            legend.position = "none",
+            axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)
+        ) +
+        ggtitle(paste0(p, ": Framing Effects on Party Polling")) +
+        labs(x = "Topic", y = "Effect Size")
+    ggsave(filename = paste0("plots/var_", p, "_topics.png"), width = 15, height = 8)
+}
+
+
+## plot single vars
[…]

### 2023-04-14 code/functions/var_topic.r
Estimate Poll-Topic VAR

@@ -1,0 +1,125 @@
+## estimate var model poll ~ topic
+var_topic <-
+    function(
+        topic,
+        party,
+        controls = NA,
+        max_lag = 12,
+        topic_metric = "association",
+        aggregation = "ym",
+        plot_var = FALSE) {
+
+    ## load data
+    merged <- data.table::fread("data/processed/media/merged.csv")
+
+    ## aggregate data
+    merged_agg <-
+        merged %>%
+        mutate(
+            yw = paste(year, week(date), sep = "-"),
+            ym = paste(year, month(date), sep = "-"),
+            yq = paste(year, quarter(date), sep = "-")
+        ) %>%
+        group_by(.data[[aggregation]]) %>%
+        summarize(
+            date = min(date),
+            mig_sal = sum(mig_sal),
+            crime_sv = sum(crime_label),
+            across(contains("Assoc"), ~mean(.x, na.rm = T)),
+            across(AfD:Union, ~mean(.x, na.rm = T)),
+            across(`AfD Topic`:`Young Refugees`, ~sum(.x, na.rm = T)),
+            across(`(ot) Abschiebung 1`:`(ot) Koalitionsstreit über Transitzonen`, ~sum(.x, na.rm = T))
+        ) %>%
+        mutate(
+            year = year(date),
+            week = week(date),
+            wday = wday(date)
+            )
+
+    ## define topic metric
+    if(topic_metric == "association") {
+        if (grepl(topic, pattern = "\\(ot\\)")) {
+            topic_var <- paste0("Association ", topic)
+        } else {
+            topic_var <- paste0("Association (reduced): ", topic)
+        }
+    }
+                    
+
+    if (topic_metric == "share"){
+        merged_agg[topic_var] <-
+            merged_agg[topic_var] / merged_agg["mig_sal"]
+    }
+
+    ## filter missings
+    merged_agg <-
+        merged_agg[min((seq_len(nrow(merged_agg)))[!is.na(merged_agg[[party]])]):max((1:nrow(merged_agg))[!is.na(merged_agg[[party]])]),] # drop front and end missing values
+
+    ## interpolate missing values
+    merged_agg[party] <- zoo::na.approx(merged_agg[party])
+
+    ## filter missings
+    merged_agg <-
[…]

### 2023-04-14 code/preprocessing/merging.r
Merge topic-polling data

@@ -1,0 +1,86 @@
+## run var models of polling and topics in migration coverage
+library(tidyverse)
+library(vars)
+library(data.table)
+library(zoo)
+
+topics  <- fread("data/processed/media/docs_topics_sims.csv")
+polls <- fread("data/raw/polls/polls.csv")
+
+## generate topic dummies
+topics_agg  <- 
+    topics[,c("date_clean", "paper", "dpa", "crime_label", "crime_prob")] %>%
+    cbind(fastDummies::dummy_cols(topics$reduced_topic_label)) %>%
+    mutate(reduced_topic_label = `.data`)
+
+## clean colnames
+colnames(topics_agg) <- 
+    colnames(topics_agg) %>%
+    str_replace(".data_", "")
+
+topics_agg <- 
+    topics_agg %>%
+    dplyr::select(!contains(".data"), -reduced_topic_label)
+
+## add original topic labels
+topics_agg <-
+    topics_agg %>% 
+    cbind(fastDummies::dummy_cols(topics$topic_label)) %>% 
+    mutate(topic_label = `.data`)
+
+## clean colnames
+colnames(topics_agg) <- 
+    colnames(topics_agg) %>%
+    str_replace(".data_", "(ot) ")
+
+topics_agg <- 
+    topics_agg %>%
+    dplyr::select(!contains(".data"), -topic_label)
+
+## aggregate topics
+topics_agg <- 
+    topics_agg %>%
+    group_by(date_clean, paper) %>%
+    summarise(
+        across(everything(), ~sum(.x)),
+        mig_sal = n()) %>%
+    dplyr::select(-paper) %>%
+    group_by(date_clean) %>%
+    summarise_all(sum)
+
+
+## merge daily polls and topics
+topics_agg <-
+    topics %>%
+    dplyr::select(c(paper, date_clean, contains("Association"))) %>%
+    group_by(date_clean, paper) %>%
+    summarise_all(mean) %>%
+    dplyr::select(!paper) %>%
+    group_by(date_clean) %>%
+    summarise_all(mean) %>%
+    dplyr::select(-date_clean) %>%
+    cbind(topics_agg) %>%
+    mutate(date = date_clean)
+
+polls_agg <-
+    polls %>%
+    dplyr::select(c(date, party, value)) %>%
+    group_by(date, party) %>%
+    summarise_all(mean) %>%
+    mutate(value = value/100) %>%
+    pivot_wider(
+        names_from = party,
+        values_from = value
+    )
+
+merged <-
[…]

### 2023-04-14 code/estimation/topic_var.r
incorporate original topics in var

@@ -21,7 +21,8 @@ topics <-
     dplyr::select(!contains("Stock Market")) %>%
     colnames() %>%
     str_replace("Association \\(reduced\\): ", "") %>%
-    str_replace("Association ", "")
+    str_replace("Association ", "") %>%
+    str_replace("\\(ot\\)\\:", "ot")
 
 rm(merged)
 
@@ -70,8 +71,7 @@ for (i in seq_len(nrow(var_results))) {
             aggregation = var_results$aggregation[i],
             topic_metric = var_results$topic_metric[i],
             controls = var_results$controls[i],
-            max_lag = var_results$lag_max[i],
-            plot_var = FALSE
+            max_lag = var_results$lag_max[i]
         )
 
     var_results[i, c("point_party_dv", "lower_party_dv", "upper_party_dv")] <-

### 2023-04-14 code/functions/var_topic.r

@@ -6,8 +6,7 @@ var_topic <-
         controls = NA,
         max_lag = 12,
         topic_metric = "association",
-        aggregation = "ym",
-        plot_var = FALSE) {
+        aggregation = "ym") {
 
     ## load data
     merged <- data.table::fread("data/processed/media/merged.csv")
@@ -36,15 +35,21 @@ var_topic <-
             wday = wday(date)
             )
 
+    ## rename columns
+    colnames(merged_agg) <-
+        str_replace(colnames(merged_agg), "\\(ot\\)", "ot")
+
     ## define topic metric
     if(topic_metric == "association") {
-        if (grepl(topic, pattern = "\\(ot\\)")) {
-            topic_var <- paste0("Association ", topic)
+        if (grepl(topic, pattern = "\\bot\\s")) {
+            topic_var <- str_replace(topic, "\\bot", "ot\\:")
+            topic_var <- paste0("Association ", topic_var)
         } else {
             topic_var <- paste0("Association (reduced): ", topic)
         }
+    }else{
+        topic_var <- topic
     }
-                    
 
     if (topic_metric == "share"){
         merged_agg[topic_var] <-

### 2023-04-15 code/collection/get_manifestos.R
Collect Migration-Related Manifesto Content

@@ -8,43 +8,58 @@
 #  R version 4.1.1 (2021-08-10)
 # ______________________________________________
 
-# parameters ####
-whitelist <- ls()
+# setup
+library(tidyverse)
+library(dplyr)
+library(manifestoR)
+library(data.table)
 
-
-# Get data ####
+# Get data 13 & 17 elections ####
 mp_setapikey("data/raw/manifestos/manifesto_apikey.txt")
 
-my_corpus <- mp_corpus(countryname == "Germany" & 
-                         edate < as.Date("2014-01-01") & 
+my_corpus <- mp_corpus(countryname == "Germany" &
+                         edate < as.Date("2018-01-01") &
                          edate > as.Date("2013-01-01"))
 
-#
-mpds <- mp_maindataset(); clean_list <- c(clean_list, "mpds")
+mpds <- mp_maindataset()
 
-# generatae dataset ####
-corpus <- data.frame(doc_id = NULL, text = NULL)
+# generatae migration corpus ####
+corpus <- 
+  data.frame(
+    party = NULL,
+    date = NULL,
+    text = NULL, 
+    code = NULL)
 
 for (doc in names(my_corpus)){
-  
+
   text <- content(my_corpus[[doc]])
+  yr <- meta(my_corpus[[doc]])$date %>% 
+        as.character() %>% 
+        str_sub(1,4)
+  mp_codes <- codes(my_corpus[[doc]])
   partycode <- meta(my_corpus[[doc]])$party
   partyname <- mpds[mpds$party == partycode, "partyabbrev"] %>% unique() %>% .[[1]]
   
   corpus <- 
-    
     rbind(
       corpus,
       data.frame(
-        doc_id = partyname,
+        party = partyname,
+        date = yr,
+        code = mp_codes,
         text = text
       )
     )
 }
 
 # save ####
-fwrite(corpus, "data/raw/manifestos/manifestos.csv")
+fwrite(corpus, "data/raw/manifestos/manifestos1317.csv")
 
-# clean up ####
-rm(ls()[!ls() %in% whitelist])
+# mig texts only
+mig_corpus <- corpus %>%
+  filter(code %in% c("601.2", "602.2", "607.2", "608.2")) # immigration-related codes acc to CMP v5 only available for 2017
 
+table(mig_corpus$party, mig_corpus$code, mig_corpus$date) # clearly separating positions
+
+fwrite(mig_corpus, "data/raw/manifestos/manifestos1317_mig.csv")

### 2023-04-15 code/embeddings/party_embeddings.py
Estimate party embeddings and check sensibility

@@ -1,0 +1,144 @@
+#%%
+import pandas as pd
+import numpy as np
+import seaborn as sns
+from top2vec import Top2Vec
+from pprint import pprint
+import random
+random.seed(42)
+
+## load manifestos
+migmps = pd.read_csv("data/raw/manifestos/manifestos1317_mig.csv")
+
+#%% generate embeddings
+## load top2vec model
+model = Top2Vec.load("models/t2v/migration_mindocs300")
+
+## add party documents to generate embeddings
+model.add_documents(migmps["text"].tolist())
+
+#%% save new vectors
+nrows = model.document_vectors.shape[0]
+party_vecs = model.document_vectors[nrows-len(migmps.text):nrows]
+
+## merge with meta data
+party_vecs = pd.DataFrame(party_vecs)
+party_vecs = pd.concat([migmps, party_vecs], axis=1)
+
+## save party vectors (sentence embeddings)
+party_vecs.to_csv("data/processed/embeddings/parties_sentences.csv", index=False)
+
+#%% average party vectors
+vars = [i for i in range(300)]
+vars.append("party")
+party_vecs = party_vecs[vars].groupby("party").mean().reset_index()
+
+## save party vectors (average of sentence embeddings)
+party_vecs.to_csv("data/processed/embeddings/parties.csv", index=False)
+
+#%% estimate similarity to doc vecs
+
+## load doc vecs
+doc_vecs = pd.read_csv("data/processed/embeddings/documents.csv")
+
+## estimate cosin sim to reduced topics
+from scipy.spatial import distance
+cos_sim = 1 - distance.cdist(doc_vecs, party_vecs.drop("party", axis = 1), 'cosine')
+
+#%%
+## merge with meta data
+cos_sim = pd.DataFrame(cos_sim)
+cos_sim.columns = party_vecs["party"].tolist()
+
+## load meta data
+meta = pd.read_csv("data/processed/media/docs_topics_sims.csv")
+meta = meta[['paper', 'title', 'url', 'crime', 'crime_label', 'crime_prob',
+                'label_prob', 'dpa', 'date_clean', 'topic_id', 'reduced_topic_id',
+                'topic_label', 'reduced_topic_label']]
+## merge
+meta = pd.concat([meta, cos_sim], axis=1)
+
+## save
+meta.to_csv("data/processed/media/docs_party_sims.csv", index=False)
+
[…]

### 2023-05-04 pres/Presentation.qmd
Presentation Dynamics

---
title: "Does Media Framing Affect Party Performance?"
subtitle: "Presentation at the Dynamics RTG Colloquium"
author: "Nicolai Berk"
institute: "Humboldt Universität Berlin"
date: "`r Sys.Date()`"
date-format: "DD.MM.YYYY"
logo: vis/dynamics.jpg
footer: "Nicolai Berk | Media Framing and Party Performance"
format: 
  revealjs:
    theme: [simple, custom.scss]
    embed-resources: true
editor: visual
bibliography: "C:/Users/nicol/Dropbox/Studium/BibTex/PhD.bib"
---

## Motivation
```{r setup, echo=F, include=F}

library(tidyverse)
library(dplyr)

```

![Source: [Pew Research Center](https://www.pewresearch.org/fact-tank/2022/09/08/republicans-and-democrats-have-different-top-priorities-for-u-s-immigration-policy/)](vis/pewRD.png)

## Emphasis Framing

<br>

- Voters draw on different <mark>considerations</mark> when evaluating issues.
- Exposure to different considerations changes attitudes. <font size="5"> [@Nelson1997Rally]</font>
- Spatial model suggests this should translate into voting behaviour.
- Party competition research mostly concerned with issue emphasis. <font size="5"> [@GreenPedersen2019]</font>

## Contradicting Predictions

<br>

::: columns

::: {.column}

### Issue Ownership

```{mermaid}
%%{
  init: {
    'theme': 'base',
    'themeVariables': {
      'primaryColor': '#003366',
      'primaryTextColor': '#fff',
      'primaryBorderColor': '#003366',
      'lineColor': '#2171c2',
      'secondaryColor': '#2171c2',
      'tertiaryColor': '#fff'
    }
  }
}%%
flowchart LR
  A(Issue\nSalience) --> B(Party\nPosition)
  B --> C(Voting)
```

*All forms of immigration coverage benefit RR*

:::
::: {.column}

### Emphasis Framing
```{mermaid}
%%{
  init: {
    'theme': 'base',
    'themeVariables': {
      'primaryColor': '#003366',
      'primaryTextColor': '#fff',
      'primaryBorderColor': '#003366',
      'lineColor': '#2171c2',
      'secondaryColor': '#2171c2',
      'tertiaryColor': '#fff'
    }
  }
}%%
flowchart LR
  A(Frame\nPrevalence) --> B(Voter\nPosition)
  B --> C(Voting)
```

*Pro-Immigration Frames hurt RR*

:::
:::

# Empirical Strategy

## Measuring Media Framing {background-image="https://raw.githubusercontent.com/ddangelov/Top2Vec/master/images/hdbscan_docs.png" background-size="70%" background-repeat="no-repeat" background-opacity="0.3" background-position="right 0% bottom 0%"}

<br>

1. Identify migration content with supervised [BERT model](#BERT).
2. Generate <mark>document embeddings</mark> for migration articles.
3. Cluster embeddings into topics using `top2vec`.
4. Annotate based on most similar document and word vectors.

## Validation of Frame Estimates

![Different Crime Measures](../plots/Measures/crime_estimates.png)

## Validation Frame Estimates II

:::: {.columns}
::: {.column width="50%"}

![Document Level](../plots/Measures/crime_est_cor_doclevel.png)

:::

::: {.column width="50%"}

![Monthly Aggregation](../plots/Measures/crime_est_cor_monthly.png)

:::
::::

## Topic Distribution over Time

![](../plots/descriptives/topics_descriptives.png)

## Measuring Party Preferences

<br><br>

- Current: Aggregated polling from [Politico's PollOfPolls](https://www.politico.eu/europe-poll-of-polls/).
- Planned: Daily [forsa-Bus](https://search.gesis.org/?source=%7B%22query%22%3A%7B%22bool%22%3A%7B%22must%22%3A%7B%22match_all%22%3A%7B%7D%7D%2C%22filter%22%3A%5B%7B%22term%22%3A%7B%22type%22%3A%22research_data%22%7D%7D%2C%7B%22term%22%3A%7B%22study_group.keyword%22%3A%22Forsa-Bus%22%7D%7D%5D%7D%7D%7D&lang=en) polls of sample of 500 German voters.

## Party Performance

![](../plots/descriptives/polls.png){fig-align="center"}

## Estimating Effects on Party Performance

<br>

#### Inferential: RDD

Exploit events creating <mark>discontinuities</mark> in migration coverage.

<br>

#### Descriptive: VAR

Assess <mark>over-time correlation</mark> of frames and party polls.

# Preliminary Results

# Regression Discontinuity Design

## RDD

## VAR

![](../plots/var/top_topics_weekly.png)

# Conclusion

## Preliminary Summary of Results

<br><br>

- Framing *does* affect polling.
- But unclear how this generalises.

## Next Steps

<br><br>

- Get better data on dependent variable.
  - Clear RDD estimate.
  - Fine-grained VAR.
- Look for additional events.
- More validation of topics.

# Thank you!

<br>

This research is generously supported by:

::: {layout-ncol=2}

![](vis/banner_new.png)

![](vis/dfg_logo_englisch_blau_en.jpg)

:::

# Resources {visibility="uncounted"}

::: {#refs}
:::

# Appendix {visibility="uncounted"}

## Dictionary Estimates

![](../plots/var/top_dicts_weekly.png)

## Why [BERT](https://huggingface.co/docs/transformers/model_doc/bert) {#bert visibility="uncounted"}

<br>

- Pre-trained on large language corpus. <font size="5">([Details](https://www.deepset.ai/german-bert))</font> \
<font color='#801414'>➡ less training data, better performance.</font>
- Uses **contextual** embeddings. \
<font color='#801414'>➡ "fish & **chips**" vs "poker **chips**".</font>
- Outperforms humans on [SQuAD](https://rajpurkar.github.io/SQuAD-explorer/).
- SOTA in text classification.

<br>

[BACK](#measuring-media-framing)

![](vis/bertarch.png){.absolute width=400 bottom=0 right=0}

## Dealing with Imbalance {#imbalance visibility="uncounted"}

::: columns
::: {.column width="70%"}

::: callout-important
## Imbalance: Little Information in Random Samples
:::

::: callout-tip
## Informed Approach

- Generate dictionary related to outcome class.
- Extend using word embeddings to minimize bias.
- Count occurences in data.
- Draw stratified sample for subsequent training.

**Ensures overweighting of minority class.**

:::
:::

::: {.column width="30%"}

<br>

```{r, fig.height=4, fig.width=3}

counts <- 
  round(rbeta(1000, 0.2, 0.5)* 10, 0) %>%
  as_tibble() %>% 
  mutate(sample_id = cut(value, 
                         c(-Inf, 0.5, 2.5, Inf), 
                         c(1, 2, 3)),
         id = 1:n())

counts$sample_T <- rbinom(nrow(counts), 1, 0.05*(counts$value+1))

counts %>% 
  ggplot(aes(x = value)) +
  geom_histogram(aes(fill = as.character(sample_T)), bins=3) +
  scale_fill_manual(values = c("gray", "#003366"),
                    labels = c("not sampled", "sampled")) +
  theme(legend.title = element_blank(),
        legend.position = "bottom") +
  xlab("# of dict terms in text") + ylab("Observations")

```

:::
:::

[BACK](#mediadata)

### 2023-06-14 code/embeddings/party_embeddings.py
fix file paths

@@ -8,11 +8,11 @@ import random
 random.seed(42)
 
 ## load manifestos
-migmps = pd.read_csv("data/raw/manifestos/manifestos1317_mig.csv")
+migmps = pd.read_csv("../../data/raw/manifestos/manifestos1317_mig.csv")
 
 #%% generate embeddings
 ## load top2vec model
-model = Top2Vec.load("models/t2v/migration_mindocs300")
+model = Top2Vec.load("../../models/t2v/migration_mindocs300")
 
 ## add party documents to generate embeddings
 model.add_documents(migmps["text"].tolist())
@@ -26,7 +26,7 @@ party_vecs = pd.DataFrame(party_vecs)
 party_vecs = pd.concat([migmps, party_vecs], axis=1)
 
 ## save party vectors (sentence embeddings)
-party_vecs.to_csv("data/processed/embeddings/parties_sentences.csv", index=False)
+party_vecs.to_csv("../../data/processed/embeddings/parties_sentences.csv", index=False)
 
 #%% average party vectors
 vars = [i for i in range(300)]
@@ -34,12 +34,12 @@ vars.append("party")
 party_vecs = party_vecs[vars].groupby("party").mean().reset_index()
 
 ## save party vectors (average of sentence embeddings)
-party_vecs.to_csv("data/processed/embeddings/parties.csv", index=False)
+party_vecs.to_csv("../../data/processed/embeddings/parties.csv", index=False)
 
 #%% estimate similarity to doc vecs
 
 ## load doc vecs
-doc_vecs = pd.read_csv("data/processed/embeddings/documents.csv")
+doc_vecs = pd.read_csv("../../data/processed/embeddings/documents.csv")
 
 ## estimate cosin sim to reduced topics
 from scipy.spatial import distance
@@ -51,7 +51,7 @@ cos_sim = pd.DataFrame(cos_sim)
 cos_sim.columns = party_vecs["party"].tolist()
 
 ## load meta data
-meta = pd.read_csv("data/processed/media/docs_topics_sims.csv")
+meta = pd.read_csv("../../data/processed/media/docs_topics_sims.csv")
 meta = meta[['paper', 'title', 'url', 'crime', 'crime_label', 'crime_prob',
                 'label_prob', 'dpa', 'date_clean', 'topic_id', 'reduced_topic_id',
                 'topic_label', 'reduced_topic_label']]
[…]

### 2023-06-14 code/collection/get_manifestos.R
drop party similarity analyses

@@ -1,65 +1,0 @@
-# ______________________________________________
-# FrameCompetition
-# Goal: Create set of manifestos
-# Procedure: Get data, generatae dataset, save
-# ______________________________________________
-# Date:  Tue Nov 29 15:34:54 2022
-# Author: Nicolai Berk
-#  R version 4.1.1 (2021-08-10)
-# ______________________________________________
-
-# setup
-library(tidyverse)
-library(dplyr)
-library(manifestoR)
-library(data.table)
-
-# Get data 13 & 17 elections ####
-mp_setapikey("data/raw/manifestos/manifesto_apikey.txt")
-
-my_corpus <- mp_corpus(countryname == "Germany" &
-                         edate < as.Date("2018-01-01") &
-                         edate > as.Date("2013-01-01"))
-
-mpds <- mp_maindataset()
-
-# generatae migration corpus ####
-corpus <- 
-  data.frame(
-    party = NULL,
-    date = NULL,
-    text = NULL, 
-    code = NULL)
-
-for (doc in names(my_corpus)){
-
-  text <- content(my_corpus[[doc]])
-  yr <- meta(my_corpus[[doc]])$date %>% 
-        as.character() %>% 
-        str_sub(1,4)
-  mp_codes <- codes(my_corpus[[doc]])
-  partycode <- meta(my_corpus[[doc]])$party
-  partyname <- mpds[mpds$party == partycode, "partyabbrev"] %>% unique() %>% .[[1]]
-  
-  corpus <- 
-    rbind(
-      corpus,
-      data.frame(
-        party = partyname,
-        date = yr,
-        code = mp_codes,
-        text = text
-      )
-    )
-}
-
-# save ####
-fwrite(corpus, "data/raw/manifestos/manifestos1317.csv")
-
-# mig texts only
-mig_corpus <- corpus %>%
-  filter(code %in% c("601.2", "602.2", "607.2", "608.2")) # immigration-related codes acc to CMP v5 only available for 2017
-
-table(mig_corpus$party, mig_corpus$code, mig_corpus$date) # clearly separating positions
-
-fwrite(mig_corpus, "data/raw/manifestos/manifestos1317_mig.csv")

### 2023-06-14 code/embeddings/party_embeddings.py

@@ -1,484 +1,0 @@
-#%%
-import pandas as pd
-import numpy as np
-import seaborn as sns
-from top2vec import Top2Vec
-from pprint import pprint
-import random
-random.seed(42)
-
-## load manifestos
-migmps = pd.read_csv("../../data/raw/manifestos/manifestos1317_mig.csv")
-
-#%% generate embeddings
-## load top2vec model
-model = Top2Vec.load("../../models/t2v/migration_mindocs300")
-
-## add party documents to generate embeddings
-model.add_documents(migmps["text"].tolist())
-
-#%% save new vectors
-nrows = model.document_vectors.shape[0]
-party_vecs = model.document_vectors[nrows-len(migmps.text):nrows]
-
-## merge with meta data
-party_vecs = pd.DataFrame(party_vecs)
-party_vecs = pd.concat([migmps, party_vecs], axis=1)
-
-## save party vectors (sentence embeddings)
-party_vecs.to_csv("../../data/processed/embeddings/parties_sentences.csv", index=False)
-
-#%% average party vectors
-vars = [i for i in range(300)]
-vars.append("party")
-party_vecs = party_vecs[vars].groupby("party").mean().reset_index()
-
-## save party vectors (average of sentence embeddings)
-party_vecs.to_csv("../../data/processed/embeddings/parties.csv", index=False)
-
-#%% estimate similarity to doc vecs
-
-## load doc vecs
-doc_vecs = pd.read_csv("../../data/processed/embeddings/documents.csv")
-
-## estimate cosin sim to reduced topics
-from scipy.spatial import distance
-cos_sim = 1 - distance.cdist(doc_vecs, party_vecs.drop("party", axis = 1), 'cosine')
-
-#%%
-## merge with meta data
-cos_sim = pd.DataFrame(cos_sim)
-cos_sim.columns = party_vecs["party"].tolist()
-
-## load meta data
-meta = pd.read_csv("../../data/processed/media/docs_topics_sims.csv")
-meta = meta[['paper', 'title', 'url', 'crime', 'crime_label', 'crime_prob',
-                'label_prob', 'dpa', 'date_clean', 'topic_id', 'reduced_topic_id',
-                'topic_label', 'reduced_topic_label']]
-## merge
-meta = pd.concat([meta, cos_sim], axis=1)
[…]

### 2023-06-14 code/embeddings/party_frames.py

@@ -1,80 +1,0 @@
-
-
-## estimate frame prevalence in party dicts
-
-#%% setup
-
-import numpy as np
-import pandas as pd
-import nltk
-nltk.download('stopwords')
-from nltk.corpus import stopwords
-from nltk.stem.snowball import SnowballStemmer
-from sklearn.feature_extraction.text import CountVectorizer
-import spacy
-
-stemmer = SnowballStemmer('german')
-nlp = spacy.load("de_core_news_sm")
-
-sws = stopwords.words('german')
-sws.extend(['und', 'die', 'wir', 'ein', 'in', 'der', 'zu', 'ist', 'den', 'eine', 'fur', 'sich', 'nicht', 'uns', 'nach', 'das', 'mit', 'auch', 'von', 'sie', "über", "ab", "schon", "muss", "bereits", "dafür", "deshalb", "dabei", "jahr", "jahre", "jahren", "teil"])
-print(sws)
-
-
-#%% assess most prevalent uni, bi and trigrams in cmp codes
-
-### load party manifestos
-migmps = pd.read_csv("data/raw/manifestos/manifestos1317_mig.csv")
-
-### pro migration
-
-#### restrict to nouns and adjectives
-migmps['text_r'] = ''
-for row in range(migmps.shape[0]):
-    doc = nlp(migmps.text[row])
-    pos = [(w.text, w.pos_) for w in doc]
-    postxt = ''
-    for tp in pos:
-        if tp[1] == 'NOUN':
-            postxt = postxt + tp[0] + ' '
-    migmps.loc[row, "text_r"] = postxt
-
-#### stem
-migmps['stems'] = migmps.text_r.apply(lambda x: stemmer.stem(x))
-
-#### generate dfm
-vec_mig_con = CountVectorizer(min_df=3, ngram_range=(1,3))
-vec_mig_pro = CountVectorizer(min_df=3, ngram_range=(1,3))
-
-dfm_con = vec_mig_con.fit_transform(migmps.text_r[(migmps.code == 601.2) | (migmps.code == 608.2)])
-dfm_pro = vec_mig_pro.fit_transform(migmps.text_r[(migmps.code == 602.2) | (migmps.code == 607.2)])
-
-
-#%% most important terms for each category
-
-## convert dfm to pd.DataFrame
-termfreq_mig_con = pd.DataFrame(dfm_con.toarray(), columns=vec_mig_con.get_feature_names_out()).sum()
[…]

### 2023-06-14 code/preprocessing/news_sampling.R
drop duplicate preprocessing

@@ -1,15 +1,0 @@
-# ______________________________________________
-# Media Framing and Party Competition
-# Goal: Generate subsample of news corpus
-# ______________________________________________
-# Date:  Tue Nov 29 14:24:47 2022
-# Author: Nicolai Berk
-#  R version 4.1.1 (2021-08-10)
-# ______________________________________________
-
-
-
-fread("data/processed/media/news_merged.csv") %>% 
-  sample_n(10000) %>% 
-  fwrite("data/processed/media/news_merged_sample.csv")
-

### 2023-06-14 code/preprocessing/preprocess_news.R

@@ -1,87 +1,0 @@
-# ______________________________________________
-# Media Frames and Party Competition
-# Goal: Clean news coverage data
-# Procedure: load, clean, write
-# ______________________________________________
-# Date:  Tue Nov 29 12:16:17 2022
-# Author: Nicolai Berk
-#  R version 4.1.1 (2021-08-10)
-# ______________________________________________
-
-clean_list <- c()
-
-clean_list <- c(clean_list, c("corpus", "dta"))
-
-for (corpus in list.files(here("data/raw/media/newspapers"))){
-  
-  if (str_detect(corpus, "bild")){
-    
-    dta <- 
-      fread(here(paste0(here("data/raw/media/newspapers/", corpus)))) %>% 
-      mutate(date_clean = as.Date(date),
-             paper = "bild") %>%
-      select(date_clean, text, paper)
-    
-    
-  }else if (str_detect(corpus, "faz")){
-    
-    dta <- 
-      fread(here(paste0(here("data/raw/media/newspapers/", corpus)))) %>% 
-      mutate(date_clean = as.Date(date, origin = "1970-01-01"),
-             paper = "faz") %>%  # clean
-      select(date_clean, text, paper)
-    
-  }else if (str_detect(corpus, "spon")){
-    
-    dta <- 
-      fread(here(paste0(here("data/raw/media/newspapers/", corpus)))) %>% 
-      mutate(date_clean = as.Date(date, format = "%d.%m.%Y"),
-             paper = "spon") %>%  # clean
-      select(date_clean, text, paper)
-    
-  }else if (str_detect(corpus, "sz")){
-    
-    dta <- 
-      fread(here(paste0(here("data/raw/media/newspapers/", corpus)))) %>% 
-      filter(!is.na(date)) %>% 
-      mutate(date_clean = as.Date(date, origin = "1970-01-01"),
-             paper = "sz") %>%  # clean
-      select(date_clean, text, paper)
-    
-  }else if (str_detect(corpus, "taz")){
-    
-    dta <- 
-      fread(here(paste0(here("data/raw/media/newspapers/", corpus)))) %>% 
-      mutate(date_clean = as.Date(date, origin = "1970-01-01"),
-             paper = "taz") %>%  # clean
-      select(date_clean, text, paper)
-    
-  }else if (str_detect(corpus, "welt")){
-    
-    dta <- 
-      fread(here(paste0(here("data/raw/media/newspapers/", corpus)))) %>% 
[…]

### 2023-06-14 code/collection/polls.R
cleanup plot

@@ -20,16 +20,18 @@ polls_tidy <-
 
 ## plot
 plt <- polls_tidy %>%
+    filter(party != "PIRATEN") %>%
     ggplot(aes(x = date, y = value, color = party)) +
     geom_point(alpha = 0.025) +
     geom_smooth() +
     facet_wrap(~party) +
     scale_color_manual(values = 
-                        c("lightblue", "yellow", "green",
-                        "purple", "orange", "red", "blue")) +
+                        c("lightblue", "magenta", "green",
+                        "darkred", "red", "black")) +
+    guides(color = FALSE) +
     theme_minimal()
 
-png("plots/polls.png", width = 10, height = 8, units = "in", res = 300)
+png("plots/descriptives/polls.png", width = 10, height = 8, units = "in", res = 300)
 plt
 dev.off()
 

### 2023-06-14 code/estimation/granger.r
add granger causality checks

@@ -1,0 +1,92 @@
+# Granger causality checks with weekly saleince, frame attention, and voting
+
+library(tidyverse)
+library(dplyr)
+library(lmtest)
+
+## load data
+media <- 
+    data.table::fread("data/processed/media/merged.csv") %>%
+    select(
+        date_clean, AfD:Union, mig_sal,
+        `AfD Topic`, `Attacks on Refugee Homes`, `Coalition Conflict`, `Deportation`,
+        `Humanitarian Crisis Mediterranean`, `Labor Market`, 
+        `Police Action Against Human Trafficking`, `Refugee Crime`,
+        `Schengen Border Control`, `Syrian Civil War`,
+        `Welfare Migration`)
+
+media_vars <- 
+    media %>%
+    select(-date_clean, -AfD, -SPD, -GRUENE, -FDP, -Union, -PIRATEN, -LINKE) %>%
+    colnames()
+
+party_vars <- 
+    media %>%
+    select(AfD:Union, -PIRATEN) %>%
+    colnames()
+
+## daily data granger test
+ests <- 
+    expand.grid(
+        party = party_vars,
+        var = media_vars,
+        granger_p = NA,
+        reverse_p = NA
+    )
+
+for (party in party_vars){
+    for (var in media_vars){
+        ests[ests$party == party &
+                ests$var == var, "granger_p"] <- grangertest(media[[var]], media[[party]], order = 7)[2, "Pr(>F)"]
+        ests[ests$party == party &
+                ests$var == var, "reverse_p"] <- grangertest(media[[party]], media[[var]], order = 7)[2, "Pr(>F)"]
+    }
+}
+
+## save table
+write_csv(ests, "data/processed/media/granger_daily.csv")
+
+ests %>%
+    mutate(
+        granger_p = granger_p < 0.05,
+        reverse_p = reverse_p < 0.05) %>%
+    filter(granger_p | reverse_p) %>%
+    arrange(-granger_p, -reverse_p)
+
+## aggregate to weekly
+media <-
+    media %>%
+    mutate(yw = lubridate::floor_date(date_clean, "week")) %>%
+    group_by(yw) %>%
+    summarise(
+        across(AfD:Union, mean),
+        across(mig_sal:`Welfare Migration`, mean),
+    )
+
+## granger causality checks
+ests <- 
+    expand.grid(
+        party = party_vars,
+        var = media_vars,
+        granger_p = NA,
+        reverse_p = NA
+    )
+
[…]

### 2023-06-14 code/estimation/ols.r
add ols

@@ -1,0 +1,154 @@
+# ols model frames vs salience
+library(dplyr)
+library(tidyverse)
+library(data.table)
+library(here)
+
+## parameters
+first_difference <- TRUE
+outlier_removal <- TRUE
+
+if (first_difference){
+    merged <- 
+        merged %>%
+        ungroup() %>%
+        mutate(
+            across(AfD:lag_neg_tot, ~ .x - lag(.x))
+        )
+
+}
+
+merged <- 
+    merged %>%
+    mutate(across(AfD:lag_neg_tot, ~ scale(.x), .names = "{.col}_scaled"))
+
+
+
+
+## ols
+m_sal_lin <-
+    lm(LINKE  ~ lag_mig_sal, data = merged %>%
+        filter(if_all(c(LINKE_scaled, lag_mig_sal_scaled), ~ ((.x < 3 & .x > -3) | !outlier_removal))))
+        # keep IF(NOT(OUTLIER) OR NOT(REMOVAL))
+m_sal_gru <- 
+    lm(GRUENE ~ lag_mig_sal, data = merged  %>%
+        filter(if_all(c(GRUENE_scaled, lag_mig_sal_scaled), ~ ((.x < 3 & .x > -3) | !outlier_removal))))
+m_sal_spd <- lm(SPD    ~ lag_mig_sal, data = merged %>%
+                filter(if_all(c(SPD_scaled, lag_mig_sal_scaled), ~  ((.x < 3 & .x > -3) | !outlier_removal))))
+m_sal_fdp <- lm(FDP    ~ lag_mig_sal, data = merged %>% 
+                filter(if_all(c(FDP_scaled, lag_mig_sal_scaled), ~  ((.x < 3 & .x > -3) | !outlier_removal))))
+m_sal_cdu <- lm(Union  ~ lag_mig_sal, data = merged %>% 
+                filter(if_all(c(Union_scaled, lag_mig_sal_scaled), ~  ((.x < 3 & .x > -3) | !outlier_removal))))
+m_sal_afd <- lm(AfD    ~ lag_mig_sal, data = merged %>% 
+                filter(if_all(c(AfD_scaled, lag_mig_sal_scaled), ~  ((.x < 3 & .x > -3) | !outlier_removal))))
+
+ms <-
+    # modelsummary::modelsummary(
+        list(
+            "LINKE" = m_sal_lin, 
+            "GRUENE" = m_sal_gru, 
[…]

### 2023-06-14 code/estimation/topic_var.r
simplify estimation

@@ -42,17 +42,17 @@ var_results <-
         ## inputs
         topic = topics,
         party = parties,
-        controls = NA,
-        aggregation = c("yw", "ym", "yq"),
+        controls = c("mig_sal", NA),
+        aggregation = c("yw"),
         
         ## outputs
-        point_party_dv = NA,
-        lower_party_dv = NA,
-        upper_party_dv = NA,
+        point_party_iv = NA,
+        lower_party_iv = NA,
+        upper_party_iv = NA,
         
-        point_topic_dv = NA,
-        lower_topic_dv = NA,
-        upper_topic_dv = NA,
+        point_topic_iv = NA,
+        lower_topic_iv = NA,
+        upper_topic_iv = NA,
 
         stringsAsFactors = F
     ) %>%
@@ -67,7 +67,7 @@ var_results <-
         topic_metric = 
             case_when(
                 grepl(topic, pattern = "ext_") ~ "absolute",
-                !grepl(topic, pattern = "ext_") ~ "association",
+                !grepl(topic, pattern = "ext_") ~ "share",
             )
     )
 
@@ -96,4 +96,4 @@ for (i in seq_len(nrow(var_results))) {
 
 
 ## save results
-write.csv(var_results, "data/processed/estimation/var_results.csv", row.names = F)
+write.csv(var_results, "data/processed/estimation/var_results_weekly.csv", row.names = F)

### 2023-06-14 code/estimation/var_vis.r
move file

@@ -1,92 +1,0 @@
-library(tidyverse)
-library(dplyr)
-
-## load data
-var_results <- read.csv("data/processed/estimation/var_results.csv")
-
-## topics
-top_topics <- 
-    c(
-        "AfD Topic", "Refugee Arrival", "Arrival in Munich", 
-        "Attacks on Refugee Homes", "Schengen Border Control", 
-        "Refugee Crime", "Deportation", 
-        "Police Action Against Human Trafficking", 
-        "Labor Market", "Humanitarian Crisis Mediterranean", 
-        "Syrian Civil War", "Welfare Migration"
-        )
-dict_topics <- 
-    c(
-        "ext_afd", "ext_arrival", "ext_attacks", 
-        "ext_borders", "ext_crime", "ext_deportation", 
-        "ext_humantrafficking", "ext_labormarket", 
-        "ext_mediterraneancrisis", "ext_welfare"
-    )
-
-## plot topic estimates
-var_results %>%
-    filter(aggregation == "ym",
-           topic %in% top_topics) %>%
-    ggplot(aes(y = topic,
-               x = point_party_dv,
-               xmin = lower_party_dv,
-               xmax = upper_party_dv,
-               color = (lower_party_dv > 0 | upper_party_dv < 0))) +
-    geom_vline(xintercept = 0) +
-    geom_pointrange() +
-    theme_minimal() +
-    theme(legend.position = "none") +
-    facet_grid(~party, scales = "free_x") +
-    ggtitle("Framing Effects on Party Polling")
-
-ggsave(filename = "plots/var_top_topics.svg", width = 15, height = 10)
-
-## plot dict estimates
-## plot
-var_results %>%
-    filter(aggregation == "ym",
-           topic %in% dict_topics) %>%
-    mutate(topic = str_replace(topic, "ext_", "")) %>%
-    mutate(topic = toupper(topic)) %>%
-    ggplot(aes(y = topic,
-               x = point_party_dv,
-               xmin = lower_party_dv,
-               xmax = upper_party_dv,
-               color = (lower_party_dv > 0 | upper_party_dv < 0))) +
-    geom_vline(xintercept = 0) +
-    geom_pointrange() +
-    theme_minimal() +
-    theme(legend.position = "none") +
-    facet_grid(~party, scales = "free_x") +
-    ggtitle("Framing Effects on Party Polling")
-
-ggsave(filename = "plots/var_top_dicts.svg", width = 15, height = 10)
-
-
-
-
-## plot all estimates sorted by effect size per party
[…]

### 2023-06-14 code/vis/var_vis.r

@@ -1,0 +1,273 @@
+library(tidyverse)
+library(dplyr)
+
+## load data
+var_results <- read.csv("data/processed/estimation/var_results_weekly.csv")
+
+## topics
+top_topics <- 
+    c(
+        "Refugee Arrival", "Arrival in Munich", 
+        "Attacks on Refugee Homes", "Schengen Border Control", 
+        "Refugee Crime", "Deportation", 
+        "Police Action Against Human Trafficking", 
+        "Labor Market", "Humanitarian Crisis Mediterranean", 
+        "Syrian Civil War", "Welfare Migration", "AfD Topic"
+        )
+dict_topics <- 
+    c(
+        "ext_arrival", "ext_attacks", 
+        "ext_borders", "ext_crime", "ext_deportation", 
+        "ext_humantrafficking", "ext_labormarket", 
+        "ext_mediterraneancrisis", "ext_welfare", "ext_afd"
+    )
+
+
+
+
+## plot topic estimates
+var_results$controls[is.na(var_results$controls)] <- "None"
+var_results$controls[var_results$controls == "mig_sal"] <- "Salience"
+var_results$controls <- factor(var_results$controls, levels = c("None", "Salience"))
+
+var_results %>%
+    filter(aggregation == "yw",
+           topic %in% top_topics) %>%
+    ggplot(aes(y = topic,
+               x = point_topic_iv,
+               xmin = lower_topic_iv,
+               xmax = upper_topic_iv,
+               color = (lower_topic_iv > 0 | upper_topic_iv < 0),
+               shape = controls)) +
+    geom_vline(xintercept = 0) +
+    geom_pointrange(position = position_dodge(width = 0.5)) +
+    theme_minimal() +
+    theme(legend.position = "bottom") +
+    labs(colour = "p < .05", shape = "Controls") +
+    facet_grid(~party) +
+    ggtitle("Framing")
+
+ggsave(filename = "plots/var/top_topics_weekly.png", width = 10, height = 6)
+
+## plot dict estimates
+## plot
+var_results %>%
+    filter(aggregation == "yw",
+           topic %in% dict_topics) %>%
+    mutate(topic = str_replace(topic, "ext_", "")) %>%
+    mutate(topic = toupper(topic)) %>%
+    ggplot(aes(y = topic,
+               x = point_topic_iv,
+               xmin = lower_topic_iv,
[…]

### 2023-06-14 code/functions/RDDPlots.r
add rdd function

@@ -1,0 +1,181 @@
+library(tidyverse)
+library(dplyr)
+library(rdrobust)
+
+RDDPlots <- function(
+    event_name, cutoff_date, topic_ass, topic_cls_label,
+    sv, supervised, dict, plt_title
+){
+
+
+    ### polls
+    polls <- 
+        read.csv("data/processed/polls.csv") %>%
+        pivot_wider(names_from = "party", values_from = "value", values_fn = mean) %>%
+        mutate(
+            date = as.Date(date),
+            date_from = as.Date(date_from))
+
+    ### media content
+    media <- read.csv("data/processed/media/full_ests.csv") %>%
+        mutate(date_clean = as.Date(date_clean))
+
+
+    ## Cologne
+
+
+    ### Topic: Refugee Crime
+    media <- 
+        media %>%
+        mutate(topic_cls = reduced_topic_label == topic_cls_label)
+
+
+    #### models
+    m_topic_ass <- rdrobust(scale(media[, topic_ass]), as.numeric(media$date_clean - cutoff_date)) # topic association
+    m_topic_cls <- rdrobust(scale(media[, "topic_cls"]), as.numeric(media$date_clean - cutoff_date)) # topic classification
+    
+    if (!isFALSE(dict)){
+        m_dict <- rdrobust(media[, dict], as.numeric(media$date_clean - cutoff_date)) # dictionary count
+    }
+
+    if (sv){
+        if (!exists("supervised")){
+            stop("If `sv == TRUE`, need to specify `supervised`!")
+        }
+        
+        m_sv <- rdrobust(
+            scale(media[, supervised]),
+            as.numeric(media$date_clean - cutoff_date)
+            ) # supervised
+
+    }
+
+    ### Parties
+
+    #### filter overlapping polls
+    polls_sub <- 
+        polls %>%
+        filter(
+            !(
+                date > cutoff_date &
+                date_from < cutoff_date
+            )
+        )
+
+    #### models
+    m_afd   <- rdrobust(polls_sub$AfD,    as.numeric(polls_sub$date - cutoff_date))
+    m_union <- rdrobust(polls_sub$Union,  as.numeric(polls_sub$date - cutoff_date))
+    m_spd   <- rdrobust(polls_sub$SPD,    as.numeric(polls_sub$date - cutoff_date))
+    m_green <- rdrobust(polls_sub$GRUENE, as.numeric(polls_sub$date - cutoff_date))
[…]

### 2023-06-14 code/functions/var_topic.r
simplify

@@ -6,7 +6,7 @@ var_topic <-
         controls = NA,
         max_lag = 12,
         topic_metric = "association",
-        aggregation = "ym") {
+        aggregation = "date") {
 
     ## load data
     merged <- data.table::fread("data/processed/media/merged.csv")
@@ -15,9 +15,9 @@ var_topic <-
     merged_agg <-
         merged %>%
         mutate(
-            yw = paste(year, week(date), sep = "-"),
-            ym = paste(year, month(date), sep = "-"),
-            yq = paste(year, quarter(date), sep = "-")
+            yw = floor_date(date, "week"),
+            ym = floor_date(date, "month"),
+            yq = floor_date(date, "quarter")
         ) %>%
         group_by(.data[[aggregation]]) %>%
         summarize(
@@ -41,6 +41,7 @@ var_topic <-
         str_replace(colnames(merged_agg), "\\(ot\\)", "ot")
 
     ## define topic metric
+    # consider moving average for frame prevalence to deal with noisiness
     if(topic_metric == "association") {
         if (grepl(topic, pattern = "\\bot\\s")) {
             topic_var <- str_replace(topic, "\\bot", "ot\\:")
@@ -49,6 +50,7 @@ var_topic <-
             topic_var <- paste0("Association (reduced): ", topic)
         }
     }else{
+        # consider logging count
         topic_var <- topic
     }
 
@@ -64,21 +66,9 @@ var_topic <-
     ## interpolate missing values
     merged_agg[party] <- zoo::na.approx(merged_agg[party])
 
-    ## filter missings
-    merged_agg <-
-        merged_agg[min((seq_len(nrow(merged_agg)))[!is.na(merged_agg[[party]])]):max((1:nrow(merged_agg))[!is.na(merged_agg[[party]])]),] # drop front and end missing values
-
-    ## interpolate missing values
-    merged_agg[party] <- zoo::na.approx(merged_agg[party])
-
     ## define control variables
     if (!is.na(controls)) {
-        if (controls == "ywd") {
-            control_vars  <- c("year", "week", "wday")
-            control_merged_agg <- merged_agg[, c(control_vars)]
-        } else {
[…]

### 2023-06-14 code/measurement/t2v_annotation.py
split up topic estimation

@@ -1,0 +1,171 @@
+## generate topic labels
+
+## generate a dict with 62 topic labels, with keys 1-62 and assign a different category to each topic
+topic_labels = {0: "Episodisches Framing",
+                1: "Historischer Kontext",
+                2: "Unionsstreit 1",
+                3: "Bürgerkrieg in Syrien",
+                4: "Arbeitsmarkt",
+                5: "Finanzierung der Migration",
+                6: "Flüchtlingsunterbringung in Hamburg",
+                7: "Humanitäre Katastrophe im Mittelmeer",
+                8: "Bundesamt für Migration und Flüchtlinge (BAMF)",
+                9: "Trump, Mexico, Migration",
+                10: "EU Verteilung Flüchtlinge",
+                11: "Abschiebung 1",
+                12: "Unionsstreit 2",
+                13: "Aktienkurse - Dow Jones",
+                14: "Aktienkurse - DAX",
+                15: "AfD Topic",
+                16: "Lage in Griechenland (Ankunft & Lager)",
+                17: "EU-Türkei-Deal",
+                18: "Kriminalität: Gerichtsverfahren",
+                19: "Flüchtlingsunterbringung in Berlin",
+                20: "Brandanschläge auf Flüchtlingsheime",
+                21: "Grenzkontrollen durch Polizei",
+                22: "Verhandlung einer Abschiebung",
+                23: "Einwanderungszahlen",
+                24: "Migrationspolitik in Afrika",
+                25: "Koalitionsstreit über Transitzonen",
+                26: "Bundesrat Entscheidung zu sicheren Herkunftsstaate",
+                27: "Einwanderung in Sozialsysteme",
+                28: "Familiennachzug",
+                29: "Flüchtlingsprotest am Oranienplatz in Berlin",
+                30: "Abschiebung nach Afghanistan",
+                31: "Seenotrettung 1",
+                32: "Schulen",
+                33: "Kirchen",
+                34: "Balkanroute",
+                35: "Jamaikasondierung",
+                36: "Österreich",
+                37: "Umfragen",
+                38: "Fachkräftemangel",
+                39: "Kriminalität: Straftaten",
+                40: "Jugendliche Flüchtlinge",
+                41: "Marineeinsatz gegen Schleuser im Mittelmeer",
+                42: "Europäische Aktienmärkte",
+                43: "Demonstrationen",
+                44: "Boris Pistorius",
+                45: "Jesiden",
[…]

### 2023-06-14 code/measurement/top2vec.py

@@ -1,0 +1,32 @@
+## estimate topic model
+
+import pandas as pd
+import numpy as np
+from top2vec import Top2Vec
+import random
+random.seed(42)
+
+## define parameters
+umap_args = {'n_neighbors': 30, # when replicating, consider setting this to 15 (check umap website), as currently no outliers are removed
+             'n_components': 5,
+             'metric': 'cosine',
+             "random_state": 42}
+
+hdbscan_args = {'min_cluster_size': 300,
+                'min_samples':5,
+                'metric': 'euclidean',
+                'cluster_selection_method': 'eom'}
+
+## load data
+documents = pd.read_csv("data/raw/media/bert_crime_clean.csv", encoding="utf-8")["text"].to_list()
+
+## define model
+model = Top2Vec(documents= documents, 
+                # speed='deep-learn', 
+                workers=7, 
+                min_count = 100, 
+                # embedding_model='distiluse-base-multilingual-cased', 
+                umap_args = umap_args, 
+                hdbscan_args = hdbscan_args)
+
+model.save("models/t2v/migration_mindocs300")

### 2023-06-14 code/preprocessing/t2v_documentvectors.py

@@ -1,0 +1,14 @@
+import pandas as pd
+import numpy as np
+from top2vec import Top2Vec
+
+
+## set path
+import os
+os.chdir("C://Users/nicol/Dropbox/PhD/Papers/FrameCompetition")
+
+## read model
+model = Top2Vec.load("models/t2v/migration_mindocs300")
+
+## write document vectors
+pd.DataFrame(model.document_vectors).to_csv("data/processed/embeddings/documents.csv", index=False)

### 2023-06-14 code/preprocessing/t2v_labeling.py

@@ -1,0 +1,99 @@
+## label topics
+
+import pandas as pd
+import numpy as np
+import seaborn as sns
+from top2vec import Top2Vec
+from pprint import pprint
+import random
+random.seed(42)
+import json
+
+import os
+os.chdir("C://Users/nicol/Dropbox/PhD/Papers/FrameCompetition")
+
+## load model
+model = Top2Vec.load("models/t2v/migration_mindocs300")
+
+## get topic number k
+topic_nums = model.get_num_topics()
+
+## print most similar documents and topic words
+with open("data/processed/topic_docs.txt", "w", encoding="UTF-8") as f:
+    for topic in range(topic_nums):
+        documents, document_scores, document_ids = model.search_documents_by_topic(topic_num=topic, num_docs=5)
+        f.write(f"Topic: {topic}")
+        f.write(" ".join(model.topic_words[topic][:10]))
+        for doc, score, doc_id in zip(documents, document_scores, document_ids):
+            f.write("\\n")
+            f.write("\\n")
+            f.write(f"Document: {doc_id}, Score: {score}")
+            f.write("\\n")
+            f.write("-----------")
+            f.write(doc)
+            f.write("\\n")
+            f.write("-----------")
+
+## load topic ids from json
+with open('data/processed/reduced_topic_ids.json', 'r') as f:
+  reduced_ids = json.load(f)
+
+## load topic labels from json
+with open('data/processed/topic_labels.json', 'r') as f:
+    topic_labels = json.load(f)
+
+## load reduced topic labels from json
+with open('data/processed/reduced_topic_labels.json', 'r') as f:
+    reduced_labels = json.load(f)
+
+## load document metadata
+meta = pd.read_csv("data/raw/media/bert_crime_clean.csv", encoding="utf-8").drop('text', axis=1)
+
+## merge topic ids
+
+## add topic data
+meta['topic_id'] = model.get_documents_topics(model.document_ids)[0]
+meta['reduced_topic_id'] = meta['topic_id'].apply(lambda x: [i for i, j in reduced_ids.items() if x in j])
+meta.reduced_topic_id = meta.reduced_topic_id.apply(lambda x: x[0])
+meta['topic_label'] = [topic_labels[str(k)] for k in meta.topic_id]
[…]

### 2023-06-14 code/preprocessing/t2v_topicvectors.py

@@ -1,0 +1,27 @@
+## generate topic vectors
+import pandas as pd
+import numpy as np
+from top2vec import Top2Vec
+import json
+
+## set path
+import os
+os.chdir("C://Users/nicol/Dropbox/PhD/Papers/FrameCompetition")
+
+## load t2v model
+model = Top2Vec.load("models/t2v/migration_mindocs300")
+
+## load topic ids from json
+with open('data/processed/reduced_topic_ids.json', 'r') as f:
+    reduced_ids = json.load(f)
+
+
+## generate reduced topic vectors
+rt_vectors = pd.DataFrame()
+for rt in reduced_ids.keys():
+    ots = reduced_ids[rt] # get original topic ids
+    ot_vectors = model.topic_vectors[ots] # get original topic vectors
+    rt_vector = np.mean(ot_vectors, axis=0) # calculate reduced topic vector
+    rt_vectors = pd.concat([rt_vectors, pd.DataFrame(rt_vector).T], axis=0) # add to dataframe
+
+rt_vectors.to_csv("data/processed/embeddings/reduced_topics.csv", index=False)

### 2023-06-14 code/measurement/dicts_count.r
simplify, add valence

@@ -8,7 +8,7 @@ library(data.table)
 mig_artcls <-
     fread("data/raw/media/bert_crime_clean.csv", header = TRUE) %>% 
     as_tibble() %>%
-    select(!V1)
+    dplyr::select(-V1)
 
 # count terms
 
@@ -33,6 +33,30 @@ for (d in list.files("data/processed/dicts")) {
 
     }
 
+## load valence table
+topic_table <-
+    fread("data/processed/media/topic_table.csv") %>%
+    mutate(topic_label = label) %>%
+    select(topic_label, valence)
+
+## annotate valence
+top_artcls <-
+    top_artcls %>%
+    right_join(topic_table, by = "topic_label") %>%
+    mutate(
+        monthdate =
+            lubridate::floor_date(
+                as.Date(
+                    date_clean,
+                    origin = "1970-01-01"),
+                "quarter"),
+        valence =
+            factor(
+                valence,
+                levels = c("--", "-", "", "+", "++"), 
+                ordered = T),
+            )
+
 ## load topic data
 top_artcls <-
     fread("data/processed/media/docs_topics_sims.csv", header = TRUE) %>%
@@ -40,10 +64,9 @@ top_artcls <-
 
 ## merge
 merged <-
-    cbind(
-        mig_artcls %>%
-            select(contains("ext_")),
-        top_artcls)
+    mig_artcls %>%
+    right_join(top_artcls, by = c("url", "date_clean"))
+
 
 ## save
 fwrite(merged, "data/processed/media/full_ests.csv")

### 2023-06-14 code/vis/est_cor.r
add visualisation of correlations

@@ -1,0 +1,87 @@
+
+library(tidyverse)
+library(dplyr)
+library(data.table)
+
+merged <- 
+    fread("data/processed/media/full_ests.csv") %>%
+    filter(reduced_topic_label != "Stock Market")
+
+merged %>%
+    dplyr::select(date_clean, paper, crime_label, ext_crime, `Association (reduced): Refugee Crime`, reduced_topic_label) %>%
+    filter(date_clean <= "2018-12-31") %>%
+    mutate(month_date = floor_date(date_clean, "quarter")) %>%
+    group_by(month_date, paper) %>%
+    summarise(
+        crime_label = mean(crime_label, na.rm = TRUE),
+        ext_crime = mean(ext_crime >= 5, na.rm = TRUE),
+        `Association (reduced): Refugee Crime` = mean(`Association (reduced): Refugee Crime`, na.rm = TRUE),
+        reduced_topic_label = mean(reduced_topic_label == "Refugee Crime", na.rm = TRUE),
+        mig_sal = n()
+    ) %>%
+    select(-paper) %>%
+    group_by(month_date) %>%
+    summarise_all(mean) %>%
+    mutate(
+        across(!contains("month_date"), scale, )
+    ) %>%
+    ggplot(aes(x = month_date)) +
+    geom_line(aes(y = crime_label, color = "Supervised", lty = "Supervised")) +
+    geom_line(aes(y = reduced_topic_label, color = "Topic Model", lty = "Topic Model")) +
+    geom_line(aes(y = `Association (reduced): Refugee Crime`, color = "Topic Association", lty = "Topic Association")) +
+    geom_line(aes(y = ext_crime, color = "Dictionary", lty = "Dictionary")) +
+    scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
+    labs(
+        color  = "Estimate", linetype = "Estimate", shape = "Estimate",
+        x = "Date", y = "Normalized Score"
+        ) +
+    theme_minimal()
+
+# save
+ggsave("plots/crime_estimates.png", width = 10, height = 5)
+ggsave("plots/crime_estimates_pres.png", width = 8, height = 5)
+
+# correlation matrix
+library(GGally)
+ggcorr(
+    merged %>%
+        dplyr::select(contains("crime") | contains("Krim"), paper, date_clean, reduced_topic_label) %>%
+        mutate(id_var = 1:nrow(merged)) %>%
+        filter(date_clean <= "2018-12-31") %>%
+        group_by(id_var) %>%
[…]

### 2023-06-14 code/vis/rdd.r
generate rddplots

@@ -1,0 +1,330 @@
+# rdd estimates for event effects on party share
+
+library(tidyverse)
+library(dplyr)
+library(rdrobust)
+
+## load RDD funciton
+source("code/functions/RDDPlots.R")
+
+
+## Cologne and Refugee Crime
+
+plots <- RDDPlots(
+    event_name = "NYE15 Cologne",
+    cutoff_date = as.Date("2016-01-01"), # event, coverage starts later (might check difference between the two for identification of media effect)
+    topic_ass = "Association..reduced...Refugee.Crime",
+    topic_cls_label = "Refugee Crime",
+    sv = T,
+    supervised = "crime_label",
+    dict = "ext_crime",
+    plt_title = "Crime Framing"
+)
+
+plots["media_plot"]
+ggsave(paste0("plots/RDD/MediaEffect_cologne.png"), height = 4, width = 6)
+
+plots["polls_plot"]
+ggsave(paste0("plots/RDD/PollEffect_cologne.png"), height = 4, width = 6)
+
+
+## Cologne and Refugee Crime
+
+plots <- RDDPlots(
+    event_name = "Cologne Reporting",
+    cutoff_date = as.Date("2016-01-04"), # event, coverage starts later (might check difference between the two for identification of media effect)
+    topic_ass = "Association..reduced...Refugee.Crime",
+    topic_cls_label = "Refugee Crime",
+    sv = T,
+    supervised = "crime_label",
+    dict = "ext_crime",
+    plt_title = "Crime Framing"
+)
+
+plots["media_plot"]
+ggsave(paste0("plots/RDD/MediaEffect_cologne_rep.png"), height = 4, width = 6)
+
+plots["polls_plot"]
+ggsave(paste0("plots/RDD/PollEffect_cologne_rep.png"), height = 4, width = 6)
+
+
+
+## Lampedusa and the Humanitarian Crisis in the Mediterranean
+plots <- RDDPlots(
+    event_name = "Lampedusa",
+    cutoff_date = as.Date("2013-10-03"),
+    topic_ass = "Association..reduced...Humanitarian.Crisis.Mediterranean",
+    topic_cls_label = "Humanitarian Crisis Mediterranean",
+    sv = F,
+    dict = "ext_mediterraneancrisis",
+    plt_title = "Mediterranean Crisis Framing"
+)
+
+plots["media_plot"]
[…]

### 2023-06-14 pres/Presentation.qmd
move to quarto

@@
 ---
-title: "Does Media Framing Affect Party Performance?"
-subtitle: "Presentation at the Dynamics RTG Colloquium"
+title: "Framing and Voting"
+subtitle: "CompText 2023"
 author: "Nicolai Berk"
@@
 logo: vis/dynamics.jpg
-footer: "Nicolai Berk | Media Framing and Party Performance"
+footer: "Nicolai Berk | Framing and Voting"
 format: 
@@
 
-## Motivation
+# How Does Media Content Affect Voting Behaviour?
+
+## Issue Ownership
 ```{r setup, echo=F, include=F}
@@
 
-![Source: [Pew Research Center](https://www.pewresearch.org/fact-tank/2022/09/08/republicans-and-democrats-have-different-top-priorities-for-u-s-immigration-policy/)](vis/pewRD.png)
+::: {.columns}
+::: {.column width="50%"}
+
+![Source: [Conservatives Website](https://www.conservatives.com/)](vis/conservatives.png)
+
+:::
+::: {.column width="50%"}
+
+![Source: [Labour Website](https://shop.labour.org.uk/category/leaflets)](vis/LabourNHS.png)
+
+:::
+:::
 
@@
 
-<br>
+```{r frames, out.width="60%"}
 
-- Voters draw on different <mark>considerations</mark> when evaluating issues.
-- Exposure to different considerations changes attitudes. <font size="5"> [@Nelson1997Rally]</font>
-- Spatial model suggests this should translate into voting behaviour.
-- Party competition research mostly concerned with issue emphasis. <font size="5"> [@GreenPedersen2019]</font>
+library(patchwork)
 
+dta <- 
+  data.frame(
+    id = 1:100,
+    pro_frame = rnorm(10000,  1),
+    con_frame = rnorm(10000, -1)
+  )
+
+p1 <- 
+  dta %>%
+  ggplot(aes(con_frame)) +
+  geom_histogram(fill = "#e3003a") +
+  theme_minimal() +
+  labs(
+    title = "Left-leaning Frame",
+    x = "", y = ""
+  ) +
+  xlim(c(-2, 2))
+
+p2 <- 
+  dta %>%
+  ggplot(aes(pro_frame)) +
+  geom_histogram(fill = "#00b7e9") +
+  theme_minimal() +
+  labs(
+    title = "Right-leaning Frame",
+    x = "Issue Position", y = ""
+  ) +
+  xlim(c(-2, 2))
+
+p1/p2
+
+```
+<!-- 
 ## Contradicting Predictions
@@
 
-::: columns
-
-::: {.column}
-
 ### Issue Ownership
@@
 ```{mermaid}
+%%| fig-width: 10
 %%{
@@
 
-:::
-::: {.column}
+## Contradicting Predictions
+
+<br>
 
@@
 *Pro-Immigration Frames hurt RR*
-
-:::
-:::
+ -->
 
@@
 
-1. Identify migration content with supervised [BERT model](#BERT).
-2. Generate <mark>document embeddings</mark> for migration articles.
-3. Cluster embeddings into topics using `top2vec`.
-4. Annotate based on most similar document and word vectors.
+1. Collect 2.5M News Articles.
+2. Identify migration content with supervised [BERT model](#BERT).
+3. Generate <mark>document embeddings</mark> for migration articles.
+4. Cluster embeddings into topics using `top2vec`.
 
-## Validation of Frame Estimates
+## BERT Performance
 
-![Different Crime Measures](../plots/Measures/crime_estimates.png)
+<br>
 
-## Validation Frame Estimates II
+| Metric | Score |
+| :------------- |  ---- |
+| **Accuracy**       | 0.96  |
+| **Precision**      | 0.94  |
+| **Recall**         | 0.93  |
+| **F1-Score**       | 0.94  |
+
+<!-- ## Validation of Frame Estimates
+
+![Different Crime Measures](../plots/Measures/crime_estimates.png) -->
+
+## Validation Frame Estimates
 
@@
 ![](../plots/descriptives/topics_descriptives.png)
-
+<!-- 
 ## Measuring Party Preferences
@@
 - Planned: Daily [forsa-Bus](https://search.gesis.org/?source=%7B%22query%22%3A%7B%22bool%22%3A%7B%22must%22%3A%7B%22match_all%22%3A%7B%7D%7D%2C%22filter%22%3A%5B%7B%22term%22%3A%7B%22type%22%3A%22research_data%22%7D%7D%2C%7B%22term%22%3A%7B%22study_group.keyword%22%3A%22Forsa-Bus%22%7D%7D%5D%7D%7D%7D&lang=en) polls of sample of 500 German voters.
+-->
 
@@
 
-# Regression Discontinuity Design
+## Tragedy off Lampedusa: Media Effect
 
-## RDD
+![](../plots/RDD/MediaEffect_lampedusa_med.png)
+
+## Tragedy off Lampedusa: Media Effect
+
+![](../plots/RDD/PollEffect_lampedusa.png)
+
+## Parndorf Incident: Media Effect
+
+![](../plots/RDD/MediaEffect_parndorf_ht.png)
+
+## Parndorf Incident: Polling Effect
+
+![](../plots/RDD/PollEffect_parndorf.png)
 
@@
 
-# Conclusion
-
-## Preliminary Summary of Results
-
-<br><br>
-
-- Framing *does* affect polling.
-- But unclear how this generalises.
-
 ## Next Steps
@@
 
-- Get better data on dependent variable.
-  - Clear RDD estimate.
-  - Fine-grained VAR.
-- Look for additional events.
-- More validation of topics.
+- Currently waiting for daily opinion polls from [forsa-Bus](https://search.gesis.org/?source=%7B%22query%22%3A%7B%22bool%22%3A%7B%22must%22%3A%7B%22match_all%22%3A%7B%7D%7D%2C%22filter%22%3A%5B%7B%22term%22%3A%7B%22type%22%3A%22research_data%22%7D%7D%2C%7B%22term%22%3A%7B%22study_group.keyword%22%3A%22Forsa-Bus%22%7D%7D%5D%7D%7D%7D&lang=en).
+- Add control variables (esp. immigration numbers).
 
@@
 :::
-
-# Resources {visibility="uncounted"}
-
-::: {#refs}
-:::
-
-# Appendix {visibility="uncounted"}
-
-## Dictionary Estimates
-
-![](../plots/var/top_dicts_weekly.png)
-
-## Why [BERT](https://huggingface.co/docs/transformers/model_doc/bert) {#bert visibility="uncounted"}
-
-<br>
-
-- Pre-trained on large language corpus. <font size="5">([Details](https://www.deepset.ai/german-bert))</font> \
-<font color='#801414'>➡ less training data, better performance.</font>
-- Uses **contextual** embeddings. \
-<font color='#801414'>➡ "fish & **chips**" vs "poker **chips**".</font>
-- Outperforms humans on [SQuAD](https://rajpurkar.github.io/SQuAD-explorer/).
-- SOTA in text classification.
-
-<br>
-
-[BACK](#measuring-media-framing)
-
-![](vis/bertarch.png){.absolute width=400 bottom=0 right=0}
-
-## Dealing with Imbalance {#imbalance visibility="uncounted"}
-
-::: columns
-::: {.column width="70%"}
-
-::: callout-important
-## Imbalance: Little Information in Random Samples
-:::
-
-::: callout-tip
-## Informed Approach
-
-- Generate dictionary related to outcome class.
-- Extend using word embeddings to minimize bias.
-- Count occurences in data.
-- Draw stratified sample for subsequent training.
-
-**Ensures overweighting of minority class.**
-
-:::
-:::
-
-::: {.column width="30%"}
-
-<br>
-
-```{r, fig.height=4, fig.width=3}
-
-counts <- 
-  round(rbeta(1000, 0.2, 0.5)* 10, 0) %>%
-  as_tibble() %>% 
-  mutate(sample_id = cut(value, 
-                         c(-Inf, 0.5, 2.5, Inf), 
-                         c(1, 2, 3)),
-         id = 1:n())
-
-counts$sample_T <- rbinom(nrow(counts), 1, 0.05*(counts$value+1))
-
-counts %>% 
-  ggplot(aes(x = value)) +
-  geom_histogram(aes(fill = as.character(sample_T)), bins=3) +
-  scale_fill_manual(values = c("gray", "#003366"),
-                    labels = c("not sampled", "sampled")) +
-  theme(legend.title = element_blank(),
-        legend.position = "bottom") +
-  xlab("# of dict terms in text") + ylab("Observations")
-
-```
-
-:::
-:::
-
-[BACK](#mediadata)
